### 2010-04-29 trunk/paper.tex
initial commit

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\newenvironment{tightenumerate}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}
}

% this makes list spacing much better.
\newenvironment{tightitemize}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}
}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi

\begin{document}

\title{Segmentation Using Attributes}

\author{Aibo Tian\\
%Institution1\\
%Institution1 address\\
{\tt\small atian@cs.utexas.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
John Edwards\\
%Institution2\\
%First line of institution2 address\\
{\tt\small edwardsj@cs.utexas.edu}
}

\maketitle
\thispagestyle{empty}

%-------------------------------------------------------------------------------
% abstract
%-------------------------------------------------------------------------------
\begin{abstract}
Attributes have been shown to be effective in assisting object detection and
classification, and they provide means to also incorporate semantic
information available to and provided by humans.  On another front, the
combination of segmentation and object classification has been shown to
improve both segmentation and classification.  We propose to incorporate
attributes into segmentation using a hierarchical methodology.
That is, using attributes as features, we will discover attributes of regions
at all levels of a hierarchical segmentation, use a voting scheme to
boost attributes based on relative location probability maps,
incorporate hierarchical confidences in determining a confidence for
a given region, and employ a min-cut solution to a CRF to determine
final confidences at the lowest segmentation level.

We will initially test the system by determining only
figure and ground (not multiple labelings) where the only object class
is a car.
\end{abstract}

%-------------------------------------------------------------------------------
% introduction
%-------------------------------------------------------------------------------
\section{Introduction}
Here is the introduction.

%-------------------------------------------------------------------------------
% related work
%-------------------------------------------------------------------------------
\section{Related work}
A significant amount of recent work has been done in the area of using
attributes as high-level features for image classification and object
description \cite{farhadi09, lampert09, kumar09}.  
Another area of computer vision, that of segmentation,
has seen a resurgence of popularity as methods to incorporate top-down
information into segmentation have been shown to be highly effective
\cite{borenstein04, pantofaru, gu09, russell06, malisiewicz, leibe04, hoiem05, shotton06}.  
We propose to leverage research done in both of these areas -- attributes
and top-down/bottom-up segmentation -- to produce a combined approach.

Farhadi et al
\cite{farhadi09} use attributes as high-level features for object classification. They
can also describe an image using its attributes alone.
Lampert et al \cite{lampert09}
use the attributes as a intermediate layer between the low-level
features and object classes. Based on this layer, they can predict
disjoint classes that are not seen in the training set.  Both of these
approaches are geared toward object detection and classification.  While
our method goes further, incorporating segmentation, we will be using
the ideas and algorithms in \cite{farhadi09} for assignments of 
attributes to different segmented regions.

Object classification can give some top-down high-level information
for segmentation. On the other hand, segmentation can provide
image-based coherence information for classification. To deal with
the problem that the bottom-up single segmentation is not accurate,
more and more algorithms are based on multiple segmentations. Gu et
al \cite{gu09} uses the hierarchical segmentation algorithm to
generate multiple segments, and detect different parts of objects in
each segment. The final objects are voted for by the various parts.
We will initially be using the same segmentation algorithm used in
this paper, but without discarding the hierarchy.
Russell et al \cite{russell06} detect the whole object in each of
the multiple segment, by assuming that most objects get segmented
correctly at least once during the multiple segmentation. Our approach
will be far less aggressive in that we will use object classes and 
features (attributes in our case) that are known \emph{a priori}.
Pantofaru et
al \cite{pantofaru} use three different segmentation algorithms to
generate the multiple segments. After detecting objects in each
segment, they merge the intersected segments as final results. In
our method, we use common knowledge of distribution of attributes to
merge segments.
Borenstein et al \cite{borenstein04} proposed a method of combining top-down
and bottom-up information to generate a high-quality segmentation.  Their
approach to the top-down is to use exemplar image fragments and match them
to the image and then refining the top-down segmentation using their
segmentation hierarchy.  Our approach is very similar to this in spirit.
While our initial estimate of segmentation is from the bottom-up (while
theirs is from the top-down) we will use the hierarchical information
from the segmentation to boost confidences of segmentation at the lowest
level, similar to what they do.

Another interesting work is that of Gould et al \cite{gould08}.  They use
superpixels for an initial segmentation, build a CRF that includes a
relative location feature in the energy function and minimizes the CRF
for a final segmentation.  The relative location feature is determined
using prior location probability maps.  Our approach is similar to this
as well, in that we will also incorporate relative location information,
although ours will use attributes' relative locations rather than object
classes.  We will also use a CRF for the final segmentation, but will
use a min-cut solution since our labels are binary.
Kumar et al \cite{kumar05} incorporate shape structure into the segmentation by
adding a latent shape parameter to the CRF.  This seems like it would be
a useful addition to our system but make the scope too large.

%-------------------------------------------------------------------------------
% technical approach
%-------------------------------------------------------------------------------
\section{Technical approach}
We will assume that we know that an object is present in the image, as is done in \cite{borenstein04}, as opposed to no knowledge, as in \cite{shotton06}.  So we will have to use tagged examples.

The labeling will be binary - imageground and background, as opposed to multi-label results.

We'll use a conditional Markov Random Field (CRF) similar to \cite{gould08}.  The CRF will encode the neighborhood structure/adjacency naturally.

We need to decide whether to use superpixels, as in \cite{gould08} or bag of regions as in \cite{gu09, russell06}, and whether to maintain hierarchy or not.  Another approach to consider is in \cite{hoiem05}.

We have to be careful on attribute definitions, to decide exactly where they lie on the feature spectrum.  I think we should restrict ourselves to labeling cars, and thus the attributes will be things like wheel, door, window, headlight, running board, taillight, etc.

%\begin{figure}
%\center
%\includegraphics[width=0.80\textwidth]{flowchart.eps}
%\caption{Flow chart of testing phase of our algorithm}
%\label{fig:flow}
%\end{figure}
%
%Figure \ref{fig:flow} shows the basic elements of the testing phase of our algorithm.  
%We begin by hierarchically segmenting the image, retaining the hierarchy of the
%segmentation.  Each segment, or region, is then assigned attributes using the algorithm
%found in \cite{farhadi09}.  We will use the code for this algorithm that is 
%provided by the authors.  
%
%Once we have attributes assigned to each region we set up
%the CRF.  The energy function will look something like this:
%
%\begin{equation}
%\psi(\mb{m}) = \sum_i{\left(\phi(I|m_i)+ \sum_j{f^{\mathsf{pair}}(m_i,m_j,I)} \right)}
%\end{equation}
%
%where
%
%\begin{equation}
%\phi(I|m_i) = f^{\mathsf{relloc}}(S_i, c_i, I) + f^{\mathsf{app}}(S_i, c_i, I)
%\end{equation}
%
%$f^{\mathsf{relloc}}(S_i, c_i, I)$ and $f^{\mathsf{app}}(S_i, c_i, I)$ are defined much in 
%the same spirit as they are in \cite{gould08}.  The relative location feature 
%function requires relative location probability maps which we may build by hand
%or learn (see Tasks section below).  The features will be built from the probability
%maps using a voting scheme as in \cite{gould08}.
%
%We are still unsure what the smoothness function 
%$f^{\mathsf{pair}}(m_i,m_j,I)}$ will look like.  We may learn pairwise attribute
%affinity weights or simply determine a weight based on how many car attributes
%the two regions $S_i$ and $S_j$ have.
%
%As we've chosen to do a binary segmentation (figure, ground) we can use a min-cut-based
%algorithm \cite{boykov01} for the energy minimization of the CRF.  We hope to be able
%to use existing code for this (we can't use the code in \cite{gould08} as they don't
%use min-cut), but have not yet looked carefully.
%
%Once the CRF is in place, we run the energy minimization which gives us the
%segmentation with the estimated highest posterior (if we understand it
%correctly).

%-------------------------------------------------------------------------------
% experimental results
%-------------------------------------------------------------------------------
\section{Experimental results}
Here are some results.

%-------------------------------------------------------------------------------
% conclusions and future work
%-------------------------------------------------------------------------------
\section{Conclusions and future work}
Here are some conclusions.

%-------------------------------------------------------------------------------
% bibliography
%-------------------------------------------------------------------------------
{\small
%\bibliographystyle{plain}
\bibliographystyle{ieee}
\bibliography{refs}
}

\end{document}

### 2010-04-30 trunk/paper.tex
changes

@@
 combination of segmentation and object classification has been shown to
-improve both segmentation and classification.  We propose to incorporate
+improve both segmentation and classification.  We present a method of incorporating
 attributes into segmentation using a hierarchical methodology.
-That is, using attributes as features, we will discover attributes of regions
-at all levels of a hierarchical segmentation, use a voting scheme to
-boost attributes based on relative location probability maps,
-incorporate hierarchical confidences in determining a confidence for
-a given region, and employ a min-cut solution to a CRF to determine
-final confidences at the lowest segmentation level.
-
-We will initially test the system by determining only
-figure and ground (not multiple labelings) where the only object class
-is a car.
+That is, using attributes as features, we discover attributes of regions
+at all levels of a hierarchical segmentation, 
+incorporate hierarchical confidences in determining a confidence that
+a given region is part of a given object, and segment the image using
+these confidences.  We also present results from experiments run using
+this method.
 \end{abstract}
@@
 \section{Introduction}
-Here is the introduction.
+Very recent work on using attributes as features \cite{farhadi09, lampert09}
+has shown that attributes are an effective way of communicating information
+about an object in an image.  Attributes are, in essence, semantic high-level
+features.  The attributes of an image are learned using low-level features,
+and once learned, they can be used in object detection and also in describing
+objects in an image that are unknown.
+
+Image segmentation is a very different field of research and has a very different
+goal - that of finding very accurate boundaries of objects in an image.
+
+Our work focuses on leveraging attributes to produce accurate segmentations.
+The idea is to find image regions with salient attribute distributions.  If
+these regions can be combined together to for larger regions with attribute 
+distributions matching some object's canonical distribution then one can
+declare the combined region an accurate segmentation for that object.
+
+In practice, however, the testing of all combinations of regions to find 
+objects is intractable.  We use two approximatory algorithms operating on
+a segmentation hierarchy to determine salient regions.  Both are subtractive
+algorithms, which first predict attributes on the entire region and then
+proceed by observing the effects of removing different regions during
+a top-down traversal of the tree.  The benefit of using these methods are
+that large regions that clearly don't contribute to attribute saliency
+can be pruned from the tree early in the traversal.  This approach avoids
+the combinatoric complexity of a full search and, even more, prunes many
+regions from the segmentation tree before they even are searched, bringing
+the computational complexity, in practice, to roughly $O(n)$ where $n$ is
+the number of leaves in the segmentation tree.
+
+While we focus on segmentation of known objects, we anticipate an application
+that takes more advantage of attributes: that of segmenting \emph{unknown}
+objects from an image that exhibit salient but unrecognized attribute
+distributions.  This type of application brings out some of the true power of
+attributes, that of assigning semantic meaning to unknown, segmented objects.
+
+This paper is organized as follows: we first discuss related work (\S \ref{sec:related_work})
+and then present the algorithm in detail (\S \ref{sec:technical}).  We then discuss results from
+a small-scale experiment on images from the pascal 2008 dataset (\S \ref{sec:results}), after which we draw
+conclusions and discuss future directions (\S \ref{sec:conclusions}).
 
@@
 \section{Related work}
+\label{sec:related_work}
 A significant amount of recent work has been done in the area of using
@@
 \section{Technical approach}
+\label{sec:technical}
+Our approach begins with building a segmentation tree.  We use the segmentation
+approach of \cite{arbelaez09} (in fact, we use their code).  This is a hierarchical
+segmentation approach which first detects contours using the \emph{gPb} detector
+\cite{maire08}.  Once the contours are detected, regions are discovered using a
+watershed algorithm after which an Ultrametric Contour Map (UCM) is constructed,
+which defines the region hierarchy.
+
+The top node of this hierarchy is the image itself.  Our algorithm first predicts
+attributes on the image.  Our attributes are trained using images from the pascal 
+2008 dataset using the same annotations used in \cite{farhadi09}.  We trained using
+an SVM with linear kernel.
+
+TO TALK ABOUT:
+? Discovered that our implementation learns largely on the object and not truly
+on the different attributes.
+
 We will assume that we know that an object is present in the image, as is done in \cite{borenstein04}, as opposed to no knowledge, as in \cite{shotton06}.  So we will have to use tagged examples.
@@
 \section{Experimental results}
+\label{sec:results}
 Here are some results.
@@
 \section{Conclusions and future work}
-Here are some conclusions.
+\label{sec:conclusions}
+Highly dependent on attribute selection and discriminatory ability of attributes.
 

### 2010-04-30 paper.tex
additions

--- 2010-04-30 trunk/paper.tex
@@
 \usepackage{amssymb}
+\usepackage{subfigure}
+\usepackage{algorithmic}
+\usepackage{algorithm}
 
@@
 declare the combined region an accurate segmentation for that object.
+
+\begin{figure}
+\label{fig:truck}
+\centering
+\subfigure[]{
+\label{fig:trucka}
+\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
+}
+\subfigure[]{
+\label{fig:truckb}
+\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
+}
+\caption{Segmentation by maximizing attribute saliency.  \subref{fig:trucka} shows
+the original image with any ``car'' attributes that were predicted.  $P$ is the probability
+that the image contains a car.  \subref{fig:truckb} shows the segmented image after
+running our segmentation tree pruning algorithm.  As extraneous regions are pruned
+more car attributes are predicted and the probability that the remaining image 
+contains a car increases.}
+\end{figure}
 
@@
 \label{sec:technical}
-Our approach begins with building a segmentation tree.  We use the segmentation
-approach of \cite{arbelaez09} (in fact, we use their code).  This is a hierarchical
-segmentation approach which first detects contours using the \emph{gPb} detector
+Our approach begins with training attribute classifiers.  We trained using
+an SVM with linear kernel.  A set of training images is annotated with objects
+contained in the image, bounding boxes for the objects, and attributes exhibited
+by the image.  We use a subset of the features used in \cite{farhadi09}, namely
+HOG, texture and color descriptors.  The HOG descriptors are quantized into 1000
+kmeans centers, and the texture and color are quantized to 256 and 128 kmeans centers,
+respectively.  Our features differ from \cite{farhadi09} in various ways.  We don't
+use edge descriptors, nor do we generate ``sub-''histograms for 6 cells in the
+image.  The presence of cell histograms would complicate matters when extracting
+features from segmented regions.
+
+Once the attribute classifiers are trained we build a segmentation tree for each
+image.  We use the segmentation
+approach of \cite{arbelaez09}.  This produces a hierarchical
+segmentation by first detecting contours using the \emph{gPb} detector
 \cite{maire08}.  Once the contours are detected, regions are discovered using a
@@
 
-The top node of this hierarchy is the image itself.  Our algorithm first predicts
-attributes on the image.  Our attributes are trained using images from the pascal 
-2008 dataset using the same annotations used in \cite{farhadi09}.  We trained using
-an SVM with linear kernel.
+We use the UCM to generate two types of region tree, shown in figure \ref{fig:tree}.
+The first tree is an additive tree, where regions are subdivided into successively
+smaller regions moving down in the tree.  We call it ``additive'' because the
+original image can be reconstructed by adding the regions from each leaf node
+together.  The figures show the nodes of the trees as containing images, but in
+truth the trees contain binary masks which, when applied to the original image,
+produce the shown node contents.
 
-TO TALK ABOUT:
-? Discovered that our implementation learns largely on the object and not truly
-on the different attributes.
+The second tree is ``subtractive.''  The tree has identical structure to the additive
+tree and each node contains the inverse of the mask of the corresponding node
+in the additive tree.
 
-We will assume that we know that an object is present in the image, as is done in \cite{borenstein04}, as opposed to no knowledge, as in \cite{shotton06}.  So we will have to use tagged examples.
+The final segmentation is obtained by pruning the region tree until a final segmentation
+meeting some criterion of absolute or relative attribute saliency is found.
+We have two methods for pruning the tree, each showing relative strengths and
+weakness.  The first is a semi-greedy additive approach which uses the additive
+tree.  The second is a greedy subtractive approach.  We now discuss each of these 
+in detail.
 
-The labeling will be binary - imageground and background, as opposed to multi-label results.
+\begin{figure*}
+\label{fig:tree}
+\centering
+\subfigure[]{
+\label{fig:treea}
+\includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
+}
+\subfigure[]{
+\label{fig:treeb}
+\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
+}
+\caption{The two segmentation hierarchies used by the additive \subref{fig:treea}
+and subtractive \subref{fig:treeb} algorithms.  The additive hierarchy breaks the
+regions into smaller and smaller regions, while the subtractive hierarchy increases
+the size of the regions as smaller and smaller chunks are removed from the image.}
+\end{figure*}
 
-We'll use a conditional Markov Random Field (CRF) similar to \cite{gould08}.  The CRF will encode the neighborhood structure/adjacency naturally.
+\subsection{Additive algorithm}
 
-We need to decide whether to use superpixels, as in \cite{gould08} or bag of regions as in \cite{gu09, russell06}, and whether to maintain hierarchy or not.
-Another approach to consider is in \cite{hoiem05}.
+Blah, blah, blah.
 
-We have to be careful on attribute definitions, to decide exactly where they lie on the feature spectrum.
-I think we should restrict ourselves to labeling cars, and thus the attributes will be things like wheel, door, window, headlight, running board, taillight, etc.
+Predicted probabilities are determined using standard histogram intersection 
+between a pattern histogram for the given object and the predicted 
+histogram for the region.
 
-%\begin{figure}
-%\center
-%\includegraphics[width=0.80\textwidth]{flowchart.eps}
-%\caption{Flow chart of testing phase of our algorithm}
-%\label{fig:flow}
-%\end{figure}
-%
-%Figure \ref{fig:flow} shows the basic elements of the testing phase of our algorithm.  
-%We begin by hierarchically segmenting the image, retaining the hierarchy of the
-%segmentation.  Each segment, or region, is then assigned attributes using the algorithm
-%found in \cite{farhadi09}.  We will use the code for this algorithm that is 
-%provided by the authors.  
-%
-%Once we have attributes assigned to each region we set up
-%the CRF.  The energy function will look something like this:
-%
-%\begin{equation}
-%\psi(\mb{m}) = \sum_i{\left(\phi(I|m_i)+ \sum_j{f^{\mathsf{pair}}(m_i,m_j,I)} \right)}
-%\end{equation}
-%
-%where
-%
-%\begin{equation}
-%\phi(I|m_i) = f^{\mathsf{relloc}}(S_i, c_i, I) + f^{\mathsf{app}}(S_i, c_i, I)
-%\end{equation}
-%
-%$f^{\mathsf{relloc}}(S_i, c_i, I)$ and $f^{\mathsf{app}}(S_i, c_i, I)$ are defined much in 
-%the same spirit as they are in \cite{gould08}.  The relative location feature 
-%function requires relative location probability maps which we may build by hand
-%or learn (see Tasks section below).  The features will be built from the probability
-%maps using a voting scheme as in \cite{gould08}.
-%
-%We are still unsure what the smoothness function 
-%$f^{\mathsf{pair}}(m_i,m_j,I)}$ will look like.  We may learn pairwise attribute
-%affinity weights or simply determine a weight based on how many car attributes
-%the two regions $S_i$ and $S_j$ have.
-%
-%As we've chosen to do a binary segmentation (figure, ground) we can use a min-cut-based
-%algorithm \cite{boykov01} for the energy minimization of the CRF.  We hope to be able
-%to use existing code for this (we can't use the code in \cite{gould08} as they don't
-%use min-cut), but have not yet looked carefully.
-%
-%Once the CRF is in place, we run the energy minimization which gives us the
-%segmentation with the estimated highest posterior (if we understand it
-%correctly).
+\[ P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}} \]
+
+\subsection{Subtractive algorithm}
+
+The subtractive algorithm relies on the idea that if removing a region from
+an image doesn't significantly affect the probability of the image containing
+the object (which probability is obtained using the predicted attribute 
+distribution) then that region can be safely removed in the final segmentation.
+The algorithm itself is shown in algorithm \ref{alg:sub_prune}.
+
+\begin{algorithm}
+\begin{algorithmic}[1]
+  \STATE \textbf{input:} 
+  \STATE \hspace{3 mm} node $n$ in segmentation tree
+  \STATE \hspace{3 mm} master mask $m_m$
+  \STATE \hspace{3 mm} probability $P_{root}$ on root node
+  \STATE \hspace{3 mm} factor $f$
+  \STATE $m_n$ := mask of $n$
+  \STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
+  \STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
+  \IF{$P_{pred} < f P_{root}$}
+    \STATE SUBTRACTIVE\_PRUNE(n.children)
+  \ELSE
+    \STATE $m_m = m_m \cap m_n$
+  \ENDIF
+\end{algorithmic}
+\caption{SUBTRACTIVE\_PRUNE}
+\label{alg:sub_prun}
+\end{algorithm}
+
+The subtractive algorithm begins at the root of the tree and predicts attributes.
+This attribute distribution and its associated probability $P_{root}$ is assumed to be
+canonical for the image.  That is, any final segmentation should not have
+significantly less probability $P_{pred}$ than $P_{root}$.  The algorithm traverses
+the subtractive tree depth-first, predicting on each node.  
+Any node that doesn't have a significant negative effect on the probability
+of the presence of the object is removed.  This test is done on line 9.  If the
+predicted probability was significantly affected, then we know that the region
+must remain.  But it doesn't mean that sub-regions might be able to be pruned
+out.  So the procedure is called recursively, checking for smaller regions
+that might be able to be pruned (line 10).
+
+If the probability was not significantly affected, then the mask is applied
+(line 12) and no recursive call is made.  This is important, because it means
+that we can remove large chunks of the image wholesale and bypass predicting
+on the node's posterity.
+
+$f$ is an important parameter that requires tuning.  Increasing $f$ makes the
+algorithm more conservative, that is, less likely to apply removals.  Decreasing
+$f$ makes it more liberal.  We found $f=0.9$ to be a reasonable value for most images.
+Figure \ref{fig:f} shows results of adjusting $f$.
+
+The runtime performance of the algorithm is dominated by the prediction step.
+Thus the advantage of pruning large chunks early is highly beneficial to 
+the runtime of the algorithm.
+
+\begin{figure}
+\centering
+\subfigure[]{
+\label{fig:fa}
+\includegraphics[width=0.22\textwidth]{figures/parking_0.9.eps}
+}
+\subfigure[]{
+\label{fig:fb}
+\includegraphics[width=0.22\textwidth]{figures/parking_1.0.eps}
+}
+\caption{Result of adjusting the factor $f$ in the subtractive algorithm.
+\subref{fig:fa} shows running the algorithm with $f=0.9$ and \subref{fig:fb}
+shows running the algorithm with $f=1.0$.  Note that \subref{fig:fb} retains
+more of the cars, especially the two closest on the right and left, but also
+hsa more false-positive pixels, such as the ceiling region of the parking
+garage.}
+\label{fig:f}
+\end{figure}
 
@@
 Here are some results.
+ trained using images from the pascal 
+2008 dataset using the same annotations used in \cite{farhadi09}.
 
@@
 Highly dependent on attribute selection and discriminatory ability of attributes.
+
+\subsection*{Acknowledgements}
+Thanks to the authors of \cite{arbelaez09} and \cite{farhadi09} for use of their
+segmentation and feature extraction code, respectively.
 

### 2010-04-30 trunk/temp3.m
precision calculation

@@ -1,0 +1,91 @@
+% temp.m
+% calculate precision
+
+% path
+BasePath='/u/atian/cv/final/code/';
+image_set='apascal';
+img_dir = [BasePath,'data/',image_set,'_images'];
+result_dir=[BasePath,'out/seg_out/'];
+
+% read bounding boxes of some class
+load('data_exp')
+cate=1; % car
+
+% get the dir of results
+result_files=dir(result_dir);
+result_files=char(result_files.name);
+result_files=result_files(4:end,:);
+result_idx=[];
+for i=1:length(result_files)
+    result_idx(i,1)=str2num(result_files(i,6:11));
+end
+
+% parameter
+par='_6_1.5_';
+
+recall_obj=[];
+precision_seg=[];
+
+for i=1:size(data_exp.names,1)
+    if (data_exp.classes{i}.class(cate)==0)
+        continue;
+    end
+    
+    img_name=data_exp.names{i};
+    img_name=regexprep(img_name, '\.jpg', '');
+    
+    img_idx=str2num(img_name(6:11));
+    
+    isExist=(result_idx==img_idx);
+    if sum(isExist)==0
+        continue;
+    end
+    
+    % get image related dir
+    result_list_dir=result_files(isExist,:);
+    result_data_dir=[];
+    for j=1:size(result_list_dir,1)
+        if strncmp(result_list_dir(j,:),[img_name,par],16)>0
+            result_data_dir=result_list_dir(j,:);
+            break;
+        end
+    end
+    if sum(size(result_data_dir))==0
+        continue;
+    end
+    
+    result_data_dir=regexprep(result_data_dir, ' ', '');
+    if exist([result_dir,result_data_dir,'/obj_seg.mat'],'file')<=0
+        continue;
+    end
+    load([result_dir,result_data_dir,'/obj_seg'])
+    % if object is not detected
+    if sum(size(obj_seg.mask))==0
+        recall_obj=[recall_obj,0];
+    else
+        recall_obj=[recall_obj,1];
+        
+        % START FROM HERE
+        % combine bounding boxes
+        groundTruth=zeros(size(obj_seg.mask));
+        bboxes=data_exp.bboxes{i}.box{cate};
+        for j=1:length(bboxes.coor)
+            temp=bboxes.coor{j};
+            groundTruth(temp(2):temp(4),temp(1):temp(3))=1;
+        end
+        
+        % get the segmentation precison
[…]

### 2010-04-30 trunk/paper.tex
paper with additive prune

@@
 %-------------------------------------------------------------------------------
-\section{Technical approach}
-\label{sec:technical}
-Our approach begins with building a segmentation tree.  We use the segmentation
-approach of \cite{arbelaez09} (in fact, we use their code).  This is a hierarchical
-segmentation approach which first detects contours using the \emph{gPb} detector
+\section{Attribute Detection}
+\label{sec:attribute}
+
+Attributes are high-level features which can reflect some semantic properties of objects.
+Given the attributes, we can do object detection based on the their distribution.
+We use the same attributes set as \cite{farhadi09}.
+This set contains three types of attributes, including Shape, Part and Material.
+All the attributes are listed in figure ?.
+
+We use similar algorithm as \cite{farhadi09} to train the attribute models.
+Three different type of features are used, such as HOG, texture and color descriptors\cite{farhadi09}.
+Those features can capture different properties.
+We use kmeans to quantize all the features.
+The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively.
+All the quantized features are concatenated to form the 1384 deminsional feature.
+
+For training, we use SVM classifier with Gaussian kernel to train model for each attribute. The precision of all the attributes on the test set is illustrated in figure?.
+
+%Our approach begins with training attribute classifiers.  We trained using
+%an SVM with linear kernel.  A set of training images is annotated with objects
+%contained in the image, bounding boxes for the objects, and attributes exhibited
+%by the image.  We use a subset of the features used in \cite{farhadi09}, namely
+%HOG, texture and color descriptors.  The HOG descriptors are quantized into 1000
+%kmeans centers, and the texture and color are quantized to 256 and 128 kmeans centers,
+%respectively.  Our features differ from \cite{farhadi09} in various ways.  We don't
+%use edge descriptors, nor do we generate ``sub-''histograms for 6 cells in the
+%image.  The presence of cell histograms would complicate matters when extracting
+%features from segmented regions.
+
+\section{Hierarchy Segmentation}
+\label{sec:segmentation}
+
+We use the segmentation
+approach of \cite{arbelaez09}.  This produces a hierarchical
+segmentation by first detecting contours using the \emph{gPb} detector
 \cite{maire08}.  Once the contours are detected, regions are discovered using a
 watershed algorithm after which an Ultrametric Contour Map (UCM) is constructed,
-which defines the region hierarchy.
+which defines the region hierarchy. Some example of the hierarchy segmentation is shown in figure?
 
-The top node of this hierarchy is the image itself.  Our algorithm first predicts
-attributes on the image.  Our attributes are trained using images from the pascal 
-2008 dataset using the same annotations used in \cite{farhadi09}.  We trained using
-an SVM with linear kernel.
+After the construction of hierarchy segmentation tree, we detect all the attributes in each node, including the intermedia node and leaf node.
+We use the output of SVM as the confidence (not binary), so each node can be represented by the confidence distribution of all attributes.
 
-TO TALK ABOUT:
-? Discovered that our implementation learns largely on the object and not truly
-on the different attributes.
+\section{Object Detection and Segmentation}
+\label{sec:detection}
 
-We will assume that we know that an object is present in the image, as is done in \cite{borenstein04}, as opposed to no knowledge, as in \cite{shotton06}.  So we will have to use tagged examples.
+Our objective is to detect object and segment it out.
+In our hierarchy segmentation tree, the problem changes to how to select those nodes belong to the desired object.
+We estimate the probability that a node is belong to object based on the attribute confidence distribution.
+For each object, we manually give the desired attribute distribution by common knowledge.
+We use the histogram intersection between the desired distribution and the estimated confidence distribution in each node as the similarity measure.
+The histogram intersection is calculated as follows:
 
-The labeling will be binary - imageground and background, as opposed to multi-label results.
+\[ HI(H_{model},H_{pred}) = \frac{|H_{model} \cap H_{pred}|}{|H_{model}|} \]
 
-We'll use a conditional Markov Random Field (CRF) similar to \cite{gould08}.  The CRF will encode the neighborhood structure/adjacency naturally.
+To select the nodes, we propose two different top-down prune algorithms, additive algorithm and subtractive algorithm.
+We use the UCM to generate two types of region tree, shown in figure \ref{fig:tree}.
+The first tree is an additive tree, where regions are subdivided into successively
+smaller regions moving down in the tree.  We call it ``additive'' because the
+original image can be reconstructed by adding the regions from each leaf node
+together.  The figures show the nodes of the trees as containing images, but in
+truth the trees contain binary masks which, when applied to the original image,
+produce the shown node contents.
 
-We need to decide whether to use superpixels, as in \cite{gould08} or bag of regions as in \cite{gu09, russell06}, and whether to maintain hierarchy or not.
-Another approach to consider is in \cite{hoiem05}.
+The second tree is ``subtractive.''  The tree has identical structure to the additive
+tree and each node contains the inverse of the mask of the corresponding node
+in the additive tree.
 
-We have to be careful on attribute definitions, to decide exactly where they lie on the feature spectrum.
-I think we should restrict ourselves to labeling cars, and thus the attributes will be things like wheel, door, window, headlight, running board, taillight, etc.
+The final segmentation is obtained by pruning the region tree until a final segmentation
+meeting some criterion of absolute or relative attribute saliency is found.
+We have two methods for pruning the tree, each showing relative strengths and
+weakness.  The first is a semi-greedy additive approach which uses the additive
+tree.  The second is a greedy subtractive approach.  We now discuss each of these 
+in detail.
 
-%\begin{figure}
-%\center
-%\includegraphics[width=0.80\textwidth]{flowchart.eps}
-%\caption{Flow chart of testing phase of our algorithm}
-%\label{fig:flow}
-%\end{figure}
-%
-%Figure \ref{fig:flow} shows the basic elements of the testing phase of our algorithm.  
-%We begin by hierarchically segmenting the image, retaining the hierarchy of the
-%segmentation.  Each segment, or region, is then assigned attributes using the algorithm
-%found in \cite{farhadi09}.  We will use the code for this algorithm that is 
-%provided by the authors.  
-%
-%Once we have attributes assigned to each region we set up
-%the CRF.  The energy function will look something like this:
-%
-%\begin{equation}
-%\psi(\mb{m}) = \sum_i{\left(\phi(I|m_i)+ \sum_j{f^{\mathsf{pair}}(m_i,m_j,I)} \right)}
-%\end{equation}
-%
-%where
-%
-%\begin{equation}
-%\phi(I|m_i) = f^{\mathsf{relloc}}(S_i, c_i, I) + f^{\mathsf{app}}(S_i, c_i, I)
-%\end{equation}
-%
-%$f^{\mathsf{relloc}}(S_i, c_i, I)$ and $f^{\mathsf{app}}(S_i, c_i, I)$ are defined much in 
-%the same spirit as they are in \cite{gould08}.  The relative location feature 
-%function requires relative location probability maps which we may build by hand
-%or learn (see Tasks section below).  The features will be built from the probability
-%maps using a voting scheme as in \cite{gould08}.
-%
-%We are still unsure what the smoothness function 
-%$f^{\mathsf{pair}}(m_i,m_j,I)}$ will look like.  We may learn pairwise attribute
-%affinity weights or simply determine a weight based on how many car attributes
-%the two regions $S_i$ and $S_j$ have.
-%
-%As we've chosen to do a binary segmentation (figure, ground) we can use a min-cut-based
-%algorithm \cite{boykov01} for the energy minimization of the CRF.  We hope to be able
-%to use existing code for this (we can't use the code in \cite{gould08} as they don't
-%use min-cut), but have not yet looked carefully.
-%
-%Once the CRF is in place, we run the energy minimization which gives us the
-%segmentation with the estimated highest posterior (if we understand it
-%correctly).
+\begin{figure*}
+\label{fig:tree}
+\centering
+\subfigure[]{
+\label{fig:treea}
+\includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
+}
+\subfigure[]{
+\label{fig:treeb}
+\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
+}
+\caption{The two segmentation hierarchies used by the additive \subref{fig:treea}
+and subtractive \subref{fig:treeb} algorithms.  The additive hierarchy breaks the
+regions into smaller and smaller regions, while the subtractive hierarchy increases
+the size of the regions as smaller and smaller chunks are removed from the image.}
+\end{figure*}
+
+\subsection{Additive algorithm}
+\label{ssec:additive}
+
+This prune algorithm is based on three observations.
+(1) At least one node in the segmentation tree contrains the whole object.
+(This is always true since the root node contains the whole image).
+(2) If both parrent node and child node have high confidence as the object, the segment of child node is more accurate than that of the parrent node.
+(3) Even if the some node has high confidence as the object, its segmentation still need to improve.
+The details of the additive algorithm is shown in alg ?.\\
+
+The idea of this algorithm is to find out the minimum discriminative segments, either positive or negative, and combine all of them together to form the final segment.
+We give three threshold for the similarity measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent perfect segment, positive segment and negative segment, respectively.
+If the similarity is above $thre\_perf$, which means the segment is a perfect object, we cut all the nodes below and return this segment.
+If the similarity is below $thre\_neg$, which means the segment is impossible to be related to the object, we cut all the nodes below too and return NULL.
+If the similarity is between $thre\_perf$ and $thre\_pos$, which means the node definitely contains the object but the segmentation is not perfect yet, we keep on checking its children nodes to refine the segmentation.
+The final case is that the similarity is between $thre\_pos$ and $thre\_neg$, which means we are not sure whether there is an object in the node, so we just keep on searching its children.
+\\
+
+The object detection is based on the output of ADDITIVE\_PRUNE.
+If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.\\
+
+(We also plan to do the vertical confidence propogation. But the experiment is too slow, we cannot incorporate it in this draft. We will show it in the final paper.)\\
+
+\begin{algorithm}
+\begin{algorithmic}
+  \STATE \textbf{input:} 
+  \STATE \hspace{3 mm} node $n$ in segmentation tree
+  \STATE \hspace{3 mm} desired object model $obj\_model$
+  \STATE \hspace{3 mm} threshold for perfect segment $thre\_perf$
+  \STATE \hspace{3 mm} threshold for positive segment $thre\_pos$
+  \STATE \hspace{3 mm} threshold for negative segment $thre\_neg$
+  \STATE \textbf{output:} 
+  \STATE \hspace{3 mm} refined segment 
+  \STATE
+  \STATE $sim=HI(obj\_model,n.conf)$
+  \IF{$sim \ge thre\_perf$}
+    \STATE return $n.segment$
+  \ENDIF
+  \IF{$sim \le thre\_neg$}
+    \STATE return $NULL$
+  \ENDIF
+  \STATE $s'=NULL$
+  \FOR{$i=1$ to $n.childNum$} 
+    \STATE s\{i\}=ADDITIVE\_PRUNE(n.children\{i\},obj\_model,...
+    \STATE ... thre\_perf,thre\_pos,thre\_neg)
+    \STATE s'=s'+s\{i\}
+  \ENDFOR
+  \IF{$sim\ge thre\_pos$ and $s'==NULL$}
+    \STATE return n.segment
+  \ELSE
+    \STATE return s'
+  \ENDIF
+\end{algorithmic}
+\caption{ADDITIVE\_PRUNE}
+\label{alg:add_prun}
+\end{algorithm}
+
+\subsection{Subtractive algorithm}
+
+The subtractive algorithm relies on the idea that if removing a region from
+an image doesn't significantly affect the probability of the image containing
+the object (which probability is obtained using the predicted attribute 
+distribution) then that region can be safely removed in the final segmentation.
+The algorithm itself is shown in algorithm \ref{alg:sub_prune}.
+
+\begin{algorithm}
+\begin{algorithmic}[1]
+  \STATE \textbf{input:} 
+  \STATE \hspace{3 mm} node $n$ in segmentation tree
+  \STATE \hspace{3 mm} master mask $m_m$
+  \STATE \hspace{3 mm} probability $P_{root}$ on root node
+  \STATE \hspace{3 mm} factor $f$
+  \STATE $m_n$ := mask of $n$
+  \STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
+  \STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
+  \IF{$P_{pred} < f P_{root}$}
+    \STATE SUBTRACTIVE\_PRUNE(n.children)
+  \ELSE
+    \STATE $m_m = m_m \cap m_n$
+  \ENDIF
+\end{algorithmic}
+\caption{SUBTRACTIVE\_PRUNE}
+\label{alg:sub_prun}
+\end{algorithm}
+
+The subtractive algorithm begins at the root of the tree and predicts attributes.
+This attribute distribution and its associated probability $P_{root}$ is assumed to be
+canonical for the image.  That is, any final segmentation should not have
+significantly less probability $P_{pred}$ than $P_{root}$.  The algorithm traverses
+the subtractive tree depth-first, predicting on each node.  
+Any node that doesn't have a significant negative effect on the probability
+of the presence of the object is removed.  This test is done on line 9.  If the
+predicted probability was significantly affected, then we know that the region
+must remain.  But it doesn't mean that sub-regions might be able to be pruned
+out.  So the procedure is called recursively, checking for smaller regions
+that might be able to be pruned (line 10).
+
+If the probability was not significantly affected, then the mask is applied
+(line 12) and no recursive call is made.  This is important, because it means
+that we can remove large chunks of the image wholesale and bypass predicting
+on the node's posterity.
+
+$f$ is an important parameter that requires tuning.  Increasing $f$ makes the
+algorithm more conservative, that is, less likely to apply removals.  Decreasing
+$f$ makes it more liberal.  We found $f=0.9$ to be a reasonable value for most images.
+Figure \ref{fig:f} shows results of adjusting $f$.
+
+The runtime performance of the algorithm is dominated by the prediction step.
+Thus the advantage of pruning large chunks early is highly beneficial to 
+the runtime of the algorithm.
+
+\begin{figure}
+\centering
+\subfigure[]{
+\label{fig:fa}
+\includegraphics[width=0.22\textwidth]{figures/parking_0.9.eps}
+}
+\subfigure[]{
+\label{fig:fb}
+\includegraphics[width=0.22\textwidth]{figures/parking_1.0.eps}
+}
+\caption{Result of adjusting the factor $f$ in the subtractive algorithm.
+\subref{fig:fa} shows running the algorithm with $f=0.9$ and \subref{fig:fb}
+shows running the algorithm with $f=1.0$.  Note that \subref{fig:fb} retains
+more of the cars, especially the two closest on the right and left, but also
+hsa more false-positive pixels, such as the ceiling region of the parking
+garage.}
+\label{fig:f}
+\end{figure}
 
@@
 \label{sec:results}
+
+In this section, we evaluate our attribute based object detection and segmentation algorithm.
+We will answer four questions.
+(1) What is the performance of object detection and segmentation?
+(2) What is the influences of different parameters?
+(3) What are the advantages of the two pruning algorithms?
+(4) Is vertical confidence propogation useful?
+
+\subsection{Dataset}
+\label{ssec:dataset}
+
+We use Pascal2008
+
 Here are some results.
+ trained using images from the pascal 
+2008 dataset using the same annotations used in \cite{farhadi09}.
 

### 2010-05-01 trunk/paper.tex
changes

@@
 a given region is part of a given object, and segment the image using
-these confidences.  We also present results from experiments run using
-this method.
+these confidences.  We also present encouraging segmentation results 
+from experiments run using this method.
 \end{abstract}
@@
 \begin{figure}
-\label{fig:truck}
 \centering
 \subfigure[]{
+\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
 \label{fig:trucka}
-\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
 }
 \subfigure[]{
+\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
 \label{fig:truckb}
-\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
 }
@@
 contains a car increases.}
+\label{fig:truck}
 \end{figure}
@@
 
-This paper is organized as follows: we first discuss related work (\S \ref{sec:related_work})
-and then present the algorithm in detail (\S \ref{sec:technical}).  We then discuss results from
-a small-scale experiment on images from the pascal 2008 dataset (\S \ref{sec:results}), after which we draw
-conclusions and discuss future directions (\S \ref{sec:conclusions}).
+%This paper is organized as follows: we first discuss related work (\S \ref{sec:related_work})
+%and then present the algorithm in detail (\S \ref{sec:technical}).  We then discuss results from
+%a small-scale experiment on images from the pascal 2008 dataset (\S \ref{sec:results}), after which we draw
+%conclusions and discuss future directions (\S \ref{sec:conclusions}).
 
@@
 \label{sec:related_work}
+[Note: this section was lifted straight from our extended abstract
+and has not yet been updated to reflect what we actually did.]
+
 A significant amount of recent work has been done in the area of using
@@
 
-Attributes are high-level features which can reflect some semantic properties of objects.
+Attributes are high-level features which can reflect semantic properties of objects.
 Given the attributes, we can do object detection based on the their distribution.
-We use the same attributes set as \cite{farhadi09}.
-This set contains three types of attributes, including Shape, Part and Material.
-All the attributes are listed in figure ?.
+We use the same attribute set as \cite{farhadi09}.
+This set contains three types of attributes, including shape, part and material.
+All attributes are listed in figure \ref{fig:atts}.
+
+\begin{figure}
+\begin{tabular}{llll}
+2D Boxy & 3D Boxy & Round & Vert Cyl \\
+Horiz Cyl & Occluded & Tail & Beak \\
+Head & Ear & Snout & Nose \\
+Mouth & Hair & Face & Eye \\
+Torso & Hand & Arm & Leg \\
+Foot/Shoe & Wing & Propeller & Jet engine \\
+Window & Row Wind & Wheel & Door \\
+Headlight & Taillight & Side mirror & Exhaust \\
+Pedal & Handlebars & Engine & Sail \\
+Mast & Text & Label & Furn. Leg \\
+Furn. Back & Furn. Seat & Furn. Arm & Horn \\
+Rein & Saddle & Leaf & Flower \\
+Stem/Trunk & Pot & Screen & Skin \\
+Metal & Plastic & Wood & Cloth \\
+Furry & Glass & Feather & Wool \\
+Clear & Shiny & Vegetation & Leather \\
+\end{tabular}
+\caption{List of attributes trained.}
+\label{fig:atts}
+\end{figure}
 
@@
 \begin{figure*}
-\label{fig:tree}
 \centering
@@
 the size of the regions as smaller and smaller chunks are removed from the image.}
+\label{fig:tree}
 \end{figure*}
@@
 
-This prune algorithm is based on three observations.
+This pruning algorithm is based on three observations.
 (1) At least one node in the segmentation tree contrains the whole object.
 (This is always true since the root node contains the whole image).
-(2) If both parrent node and child node have high confidence as the object, the segment of child node is more accurate than that of the parrent node.
-(3) Even if the some node has high confidence as the object, its segmentation still need to improve.
-The details of the additive algorithm is shown in alg ?.\\
+(2) If both parent node and child node have high confidence of containing the object, the segmentation of the child node is more accurate than that of the parrent node.
+(3) Even if the same node has high confidence of containing the object, its segmentation can still improve.
+The details of the additive algorithm is shown in algorithm \ref{alg:add_prune}.
 
-The idea of this algorithm is to find out the minimum discriminative segments, either positive or negative, and combine all of them together to form the final segment.
-We give three threshold for the similarity measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent perfect segment, positive segment and negative segment, respectively.
-If the similarity is above $thre\_perf$, which means the segment is a perfect object, we cut all the nodes below and return this segment.
-If the similarity is below $thre\_neg$, which means the segment is impossible to be related to the object, we cut all the nodes below too and return NULL.
+The idea of the algorithm is to find the smallest discriminative regions, either positive or negative, and combine all of them together to form the final segmentation.
+We use three threshold for the similarity measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent perfect segment, positive segment and negative segment, respectively.
+If the similarity is above $thre\_perf$, which means the segmentation is perfect, we cut all the nodes below and return this segment.
+If the similarity is below $thre\_neg$, which means the segment does not contain the object, we cut all the nodes below and return NULL.
 If the similarity is between $thre\_perf$ and $thre\_pos$, which means the node definitely contains the object but the segmentation is not perfect yet, we keep on checking its children nodes to refine the segmentation.
 The final case is that the similarity is between $thre\_pos$ and $thre\_neg$, which means we are not sure whether there is an object in the node, so we just keep on searching its children.
-\\
 
 The object detection is based on the output of ADDITIVE\_PRUNE.
-If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.\\
+If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.
 
-(We also plan to do the vertical confidence propogation. But the experiment is too slow, we cannot incorporate it in this draft. We will show it in the final paper.)\\
+(We also plan to do the vertical confidence propogation. But due to the slowness of the experiment, we cannot incorporate it in this draft. We will show it in the final paper.)
 
@@
 \caption{ADDITIVE\_PRUNE}
-\label{alg:add_prun}
+\label{alg:add_prune}
 \end{algorithm}
@@
 the object (which probability is obtained using the predicted attribute 
-distribution) then that region can be safely removed in the final segmentation.
+distribution and is here used interchangably used with the term ``similarity'')
+then that region can be safely removed in the final segmentation.
 The algorithm itself is shown in algorithm \ref{alg:sub_prune}.
@@
 \begin{algorithm}
-\begin{algorithmic}[1]
+\begin{algorithmic}
   \STATE \textbf{input:} 
@@
   \STATE \hspace{3 mm} master mask $m_m$
-  \STATE \hspace{3 mm} probability $P_{root}$ on root node
+  \STATE \hspace{3 mm} similarity $sim_{root}$ on root node
   \STATE \hspace{3 mm} factor $f$
   \STATE $m_n$ := mask of $n$
-  \STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
-  \STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
-  \IF{$P_{pred} < f P_{root}$}
-    \STATE SUBTRACTIVE\_PRUNE(n.children)
+  \STATE $pred\_model$ := predict attributes on image($m_n \cap m_m$)
+  \STATE $sim=HI(obj\_model,pred\_model)$
+  %\STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
+  %\STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
+  \IF{$sim < f sim_{root}$}
+    \FOR{$i=1$ to $n.childNum$} 
+      \STATE s\{i\}=SUBTRACTIVE\_PRUNE(n.children\{i\},$m_m$,
+      \STATE ...$sim_{root}$, $f$)
+    \ENDFOR
+    %\STATE SUBTRACTIVE\_PRUNE(n.children)
   \ELSE
@@
 \caption{SUBTRACTIVE\_PRUNE}
-\label{alg:sub_prun}
+\label{alg:sub_prune}
 \end{algorithm}
 
-The subtractive algorithm begins at the root of the tree and predicts attributes.
-This attribute distribution and its associated probability $P_{root}$ is assumed to be
-canonical for the image.  That is, any final segmentation should not have
-significantly less probability $P_{pred}$ than $P_{root}$.  The algorithm traverses
+The algorithm begins at the root of the tree and predicts attributes.
+This attribute distribution and its associated similarity $sim_{root}$ 
+to the object's canonical distribution is taken to be
+the standard for the image.  That is, any final segmentation should not have
+significantly less similarity $sim$ than $sim_{root}$.  The algorithm traverses
 the subtractive tree depth-first, predicting on each node.  
-Any node that doesn't have a significant negative effect on the probability
-of the presence of the object is removed.  This test is done on line 9.  If the
-predicted probability was significantly affected, then we know that the region
-must remain.  But it doesn't mean that sub-regions might be able to be pruned
-out.  So the procedure is called recursively, checking for smaller regions
-that might be able to be pruned (line 10).
+Any node that doesn't have a significant negative effect on the similarity as 
+compared to the standard is removed.  If the
+similarity was significantly affected, then we know that the region
+must remain.  But it doesn't mean that sub-regions might not be able to be pruned
+out, so the procedure is called recursively, checking for smaller regions
+that might be able to be pruned.
 
 If the probability was not significantly affected, then the mask is applied
-(line 12) and no recursive call is made.  This is important, because it means
+and no recursive call is made.  This is important, because it means
 that we can remove large chunks of the image wholesale and bypass predicting
@@
 $f$ makes it more liberal.  We found $f=0.9$ to be a reasonable value for most images.
-Figure \ref{fig:f} shows results of adjusting $f$.
+Figure \ref{fig:f} shows results of adjusting $f$ between 0.9 and 1.0.
 
@@
 
-\subsection{Dataset}
-\label{ssec:dataset}
+%\subsection{Dataset}
+%\label{ssec:dataset}
 
-We use Pascal2008
+We use the Pascal2008 dataset.  The attribute annotations used in \cite{farhadi09}
+are freely available and we used them for training the attributes.
 
-Here are some results.
- trained using images from the pascal 
-2008 dataset using the same annotations used in \cite{farhadi09}.
+\ref{table:aresults} shows some of the results from running the additive algorithm
+on all cars in the dataset.  The recall is the rate of correctly detecting
+images with cars.  The segmentation precision is calculated with
+\[ V(M_{model},M_{pred}) = \frac{|M_{model} \cap M_{pred}|}{|M_{model} \cup M_{pred}|} \]
+where $M_{model}$ is the model mask calculated from the bounding boxes
+stored with the annotations and $M_{pred}$ is the predicted segmentation
+mask.  We of course recognize that the bounding boxes are not a good measure
+of segmentation truth, but it's the best we have available.
+
+The segmentation precision for the additive algorithm
+is far better than the precision for the subtractive algorithm (which averaged
+0.09).  This is because the additive algorithm only segments images for
+which it has predicted presence of a car, so that any image pruned by the
+algorithm already has a high car similarity score, enhancing the segmentation.
+The subtractive algorithm, on the other hand, assumes presence of a car in
+the image and proceeds no matter how poor the initial similarity score is.
+(For the final paper we expect to have results comparing the precision
+of the two algorithms based only on images segmented by both.)
+
+Figures \ref{fig:good_results} and \ref{fig:bad_results} show the results
+of segmentations of various images by both images.  This shows clear linkage
+between prominence of the side profile of the car and success of the segmentation.
+It appears that the attribute classifiers are more accurate on side profiles
+than front and rear shots, although rear shots performed reasonably well when
+tail lights were not illuminated.
+
+\begin{table}
+\centering
+\begin{tabular}{|l|l|l|l|}
+\hline
+$P$ & $D$ & recall & prec \\ \hline
+4, 1 & 227 & 0.4317 & 0.2393 \\ \hline
+4, 1.5 & 239 & 0.3849 & 0.2370 \\ \hline
+6, 1.5 & 239 & 0.2720 & 0.2501 \\ \hline
+\end{tabular}
+\caption{Results from the additive algorithm on all car images.  $P$ is
+the parameters, $D$ is the number of detections, recall is the detection
+recall rate and prec is the segmentation precision on all detected
+images.}
+\label{table:aresults}
+\end{table}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008 
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:good_results}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
+Car not detected &
+\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008 
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:bad_results}
+\end{figure*}
 
@@
 %-------------------------------------------------------------------------------
-\section{Conclusions and future work}
-\label{sec:conclusions}
-Highly dependent on attribute selection and discriminatory ability of attributes.
+\section{Discussion}
+\label{sec:discussion}
+It can be seen that in simple cases both additive and subtractive algorithms
+are able to segment out rough outlines of the objects.  In most cases, even
+the more difficult ones, at least part of the car was present in the final
+segmentation.  This shows that the segmentation algorithms appear to be
+reasonable approximations to a combinatoric approach -- that of predicting
+on every combination of regions in the image.
+
+Despite these encouraging initial results, the final segmentation region 
+was often not coherent.
+This appears to be largely because the region tree approach is not
+constrained by spatial coherence.  That is, two leaf nodes containing image
+regions that are spatially next to each other may be very distant in the
+region tree.  Because of this, the attribute distribution may change significantly
+after considering the first node and before consideration of the second node.
+Another reason for this may be that our canonical attribute distribution for
+our objects gave equal weights to each attribute.  For example, a wheel was
+equally as important as shininess.  This gave unfair disadvantages to
+under-represented or ill-trained attributes.  This can be seen in the results
+where the body of the car is removed while the wheels or headlights are
+retained.
+
+As object detection is generally only as good as the features used, so also it
+appears that this approach to segmentation is only as good as the attribute
+selection and training.  We found that in images with poor segmentations, the
+confidences in prediction of car attributes were generally low.  One problem
+with this implementation of attribute classifiers was that we didn't use 
+the selection criterion described in \cite{farhadi09} that enhances within
+category prediction ability.  This means that, for example, the wheel attribute
+is highly similar to the car attribute and thus its discrimative ability
+is hurt.  One future direction for this research would be to improve the attribute
+training using the additional selection criterion and observe effects on
+the segmentations.
+
+An interesting orthogonal direction that could be taken with these ideas is to
+use segmentation using attributes as a diagnostic tool for attribute classifiers.
+That is, the segmentations produced by our algorithms can help zero in on areas
+in an image that exhibit high responses in detection of certain attributes.
+For example, an image could be segmented using similarity to a canonical distribution
+using only one attribute.  If that attribute is ``fur'' and segmentations
+consistently show paws and tails, then it would quickly become clear that
+the fur attribute classifier has learned on something other than fur.
+
+The holy grail of this approach, of course, is to be able to segment objects
+for which the canonical attribute distribution is unknown, based on a measure
+of attribute coherence.  If this can be achieved, then segmentation experiments
+could open up to non-experts, who could define coherence measures based on
+semantic attributes and then could use this approach to automatically segment large
+numbers of images even if no detection of their desired object exists.
 

### 2010-05-01 paper.tex
draft paper

@@
 a given region is part of a given object, and segment the image using
-these confidences.  We also present results from experiments run using
-this method.
+these confidences.  We also present encouraging segmentation results
+from experiments run using this method.
 \end{abstract}
@@
 \begin{figure}
-\label{fig:truck}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
+\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
+\end{figure}
+
+\begin{figure}
 \centering
 \subfigure[]{
+\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
 \label{fig:trucka}
-\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
 }
 \subfigure[]{
+\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
 \label{fig:truckb}
-\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
 }
@@
 contains a car increases.}
+\label{fig:truck}
 \end{figure}
 
-In practice, however, the testing of all combinations of regions to find 
-objects is intractable.  We use two approximatory algorithms operating on
-a segmentation hierarchy to determine salient regions.  Both are subtractive
-algorithms, which first predict attributes on the entire region and then
-proceed by observing the effects of removing different regions during
-a top-down traversal of the tree.  The benefit of using these methods are
-that large regions that clearly don't contribute to attribute saliency
-can be pruned from the tree early in the traversal.  This approach avoids
-the combinatoric complexity of a full search and, even more, prunes many
-regions from the segmentation tree before they even are searched, bringing
-the computational complexity, in practice, to roughly $O(n)$ where $n$ is
-the number of leaves in the segmentation tree.
+In practice, however, the testing of all combinations of regions to
+find objects is intractable.  We use two approximatory algorithms
+operating on a segmentation hierarchy to determine salient regions.
+Both are subtractive algorithms, which first predict attributes on
+the entire region and then proceed by observing the effects of
+removing different regions during a top-down traversal of the tree.
+The benefit of using these methods are that large regions that
+clearly don't contribute to attribute saliency can be pruned from
+the tree early in the traversal.  This approach avoids the
+combinatoric complexity of a full search and, even more, prunes many
+regions from the segmentation tree before they even are searched,
+bringing the computational complexity, in practice, to roughly
+$O(n)$ where $n$ is the number of leaves in the segmentation tree.
+The flowchart of our algorithm is shown in Figure
+\ref{fig:flowchart}.
 
@@
 %-------------------------------------------------------------------------------
-\section{Technical approach}
-\label{sec:technical}
-Our approach begins with training attribute classifiers.  We trained using
-an SVM with linear kernel.  A set of training images is annotated with objects
-contained in the image, bounding boxes for the objects, and attributes exhibited
-by the image.  We use a subset of the features used in \cite{farhadi09}, namely
-HOG, texture and color descriptors.  The HOG descriptors are quantized into 1000
-kmeans centers, and the texture and color are quantized to 256 and 128 kmeans centers,
-respectively.  Our features differ from \cite{farhadi09} in various ways.  We don't
-use edge descriptors, nor do we generate ``sub-''histograms for 6 cells in the
-image.  The presence of cell histograms would complicate matters when extracting
-features from segmented regions.
+\section{Attribute Detection}
+\label{sec:attribute}
 
-Once the attribute classifiers are trained we build a segmentation tree for each
-image.  We use the segmentation
-approach of \cite{arbelaez09}.  This produces a hierarchical
-segmentation by first detecting contours using the \emph{gPb} detector
-\cite{maire08}.  Once the contours are detected, regions are discovered using a
-watershed algorithm after which an Ultrametric Contour Map (UCM) is constructed,
-which defines the region hierarchy.
+Attributes are high-level features which can reflect semantic properties of objects.
+Given the attributes, we can do object detection based on the their distribution.
+We use the same attribute set as \cite{farhadi09}.
+This set contains three types of attributes, including shape, part and material.
+All attributes are listed in figure \ref{fig:atts}.
 
+\begin{figure}
+\begin{tabular}{llll}
+2D Boxy & 3D Boxy & Round & Vert Cyl \\
+Horiz Cyl & Occluded & Tail & Beak \\
+Head & Ear & Snout & Nose \\
+Mouth & Hair & Face & Eye \\
+Torso & Hand & Arm & Leg \\
+Foot/Shoe & Wing & Propeller & Jet engine \\
+Window & Row Wind & Wheel & Door \\
+Headlight & Taillight & Side mirror & Exhaust \\
+Pedal & Handlebars & Engine & Sail \\
+Mast & Text & Label & Furn. Leg \\
+Furn. Back & Furn. Seat & Furn. Arm & Horn \\
+Rein & Saddle & Leaf & Flower \\
+Stem/Trunk & Pot & Screen & Skin \\
+Metal & Plastic & Wood & Cloth \\
+Furry & Glass & Feather & Wool \\
+Clear & Shiny & Vegetation & Leather \\
+\end{tabular}
+\caption{List of attributes trained.}
+\label{fig:atts}
+\end{figure}
+
+We use similar algorithm as \cite{farhadi09} to train the attribute models.
+Three different type of features are used, such as HOG, texture and color descriptors\cite{farhadi09}.
+Those features can capture different properties.
+We use kmeans to quantize all the features.
+The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively.
+All the quantized features are concatenated to form the 1384 deminsional feature.
+
+For training, we use SVM classifier with Gaussian kernel to train
+model for each attribute.
+
+%The precision of all the attributes on the test set is illustrated
+%in figure?.
+
+%Our approach begins with training attribute classifiers.  We trained using
+%an SVM with linear kernel.  A set of training images is annotated with objects
+%contained in the image, bounding boxes for the objects, and attributes exhibited
+%by the image.  We use a subset of the features used in \cite{farhadi09}, namely
+%HOG, texture and color descriptors.  The HOG descriptors are quantized into 1000
+%kmeans centers, and the texture and color are quantized to 256 and 128 kmeans centers,
+%respectively.  Our features differ from \cite{farhadi09} in various ways.  We don't
+%use edge descriptors, nor do we generate ``sub-''histograms for 6 cells in the
+%image.  The presence of cell histograms would complicate matters when extracting
+%features from segmented regions.
+
+\section{Hierarchy Segmentation}
+\label{sec:segmentation}
+
+We use the segmentation approach of \cite{arbelaez09}.  This
+produces a hierarchical segmentation by first detecting contours
+using the \emph{gPb} detector \cite{maire08}.  Once the contours are
+detected, regions are discovered using a watershed algorithm after
+which an Ultrametric Contour Map (UCM) is constructed, which defines
+the region hierarchy. Some example of the hierarchy segmentation is
+shown in Figure \ref{fig:tree}.
+
+After the construction of hierarchy segmentation tree, we detect all
+the attributes in each node, including the intermediate node and
+leaf node. We use the output of SVM as the confidence (not binary),
+so each node can be represented by the confidence distribution of
+all attributes.
+
+\section{Object Detection and Segmentation}
+\label{sec:detection}
+
+Our objective is to detect object and segment it out. In our
+hierarchy segmentation tree, the problem changes to how to select
+those nodes belong to the desired object. We estimate the
+probability that a node is belong to object based on the attribute
+confidence distribution. For each object, we manually give the
+desired attribute distribution by common knowledge. We use the
+histogram intersection between the desired distribution and the
+estimated confidence distribution in each node as the similarity
+measure. The histogram intersection is calculated as follows:
+
+\[ HI(H_{model},H_{pred}) = \frac{|H_{model} \cap H_{pred}|}{|H_{model}|}
+\] ,
+
+where $H_{model}$ and $H_{pred}$ represent the desired attribute
+distribution and predicted distribution.
+
+To select the nodes, we propose two different top-down prune algorithms, additive algorithm and subtractive algorithm.
 We use the UCM to generate two types of region tree, shown in figure \ref{fig:tree}.
@@
 \subsection{Additive algorithm}
+\label{ssec:additive}
 
-Blah, blah, blah.
+This pruning algorithm is based on three observations. (1) At least
+one node in the segmentation tree contrains the whole object. (This
+is always true since the root node contains the whole image). (2) If
+both parent node and child node have high confidence of containing
+the object, the segmentation of the child node is more accurate than
+that of the parrent node. (3) Even if some node has high confidence
+of containing the object, its segmentation can still be improved by
+removing irrelevant children node. The details of the additive
+algorithm is shown in algorithm \ref{alg:add_prune}.
 
-Predicted probabilities are determined using standard histogram intersection 
-between a pattern histogram for the given object and the predicted 
-histogram for the region.
+The idea of the algorithm is to find the smallest discriminative
+regions, either positive or negative. We combine all the smallest
+positive regions while remove all the negative ones to form the
+final segmentation. We use three threshold for the similarity
+measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent
+perfect segment, positive segment and negative segment,
+respectively. If the similarity is above $thre\_perf$, which means
+the segmentation is perfect for the object, we cut all the nodes
+below and return this segment. If the similarity is below
+$thre\_neg$, which means the segment does not contain the object, we
+cut all the nodes below and return NULL. If the similarity is
+between $thre\_perf$ and $thre\_pos$, which means the node
+definitely contains the object but the segmentation is not perfect
+yet, we keep on checking its children nodes to refine the
+segmentation. The final case is that the similarity is between
+$thre\_pos$ and $thre\_neg$, which means we are not sure whether
+there is an object in the node, so we just keep on searching its
+children.
 
-\[ P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}} \]
+The object detection is based on the output of ADDITIVE\_PRUNE.
+If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.
+
+(We also plan to do the vertical confidence propogation. But due to the slowness of the experiment, we cannot incorporate it in this draft. We will show it in the final paper.)
+
+\begin{algorithm}
+\begin{algorithmic}
+  \STATE \textbf{input:}
+  \STATE \hspace{3 mm} node $n$ in segmentation tree
+  \STATE \hspace{3 mm} desired object model $obj\_model$
+  \STATE \hspace{3 mm} threshold for perfect segment $thre\_perf$
+  \STATE \hspace{3 mm} threshold for positive segment $thre\_pos$
+  \STATE \hspace{3 mm} threshold for negative segment $thre\_neg$
+  \STATE \textbf{output:}
+  \STATE \hspace{3 mm} refined segment
+  \STATE
+  \STATE $sim=HI(obj\_model,n.conf)$
+  \IF{$sim \ge thre\_perf$}
+    \STATE return $n.segment$
+  \ENDIF
+  \IF{$sim \le thre\_neg$}
+    \STATE return $NULL$
+  \ENDIF
+  \STATE $s'=NULL$
+  \FOR{$i=1$ to $n.childNum$}
+    \STATE s\{i\}=ADDITIVE\_PRUNE(n.children\{i\},obj\_model,...
+    \STATE ... thre\_perf,thre\_pos,thre\_neg)
+    \STATE s'=s'+s\{i\}
+  \ENDFOR
+  \IF{$sim\ge thre\_pos$ and $s'==NULL$}
+    \STATE return n.segment
+  \ELSE
+    \STATE return s'
+  \ENDIF
+\end{algorithmic}
+\caption{ADDITIVE\_PRUNE}
+\label{alg:add_prune}
+\end{algorithm}
 
@@
 the object (which probability is obtained using the predicted attribute
-distribution) then that region can be safely removed in the final segmentation.
+distribution and is here used interchangably used with the term ``similarity'')
+then that region can be safely removed in the final segmentation.
 The algorithm itself is shown in algorithm \ref{alg:sub_prune}.
@@
 \begin{algorithm}
-\begin{algorithmic}[1]
+\begin{algorithmic}
   \STATE \textbf{input:}
@@
   \STATE \hspace{3 mm} master mask $m_m$
-  \STATE \hspace{3 mm} probability $P_{root}$ on root node
+  \STATE \hspace{3 mm} similarity $sim_{root}$ on root node
   \STATE \hspace{3 mm} factor $f$
+  \STATE \textbf{output:}
+  \STATE \hspace{3 mm} $m_m$
+  \STATE
   \STATE $m_n$ := mask of $n$
-  \STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
-  \STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
-  \IF{$P_{pred} < f P_{root}$}
-    \STATE SUBTRACTIVE\_PRUNE(n.children)
+  \STATE $pred\_model$ := predict attributes on image($m_n \cap m_m$)
+  \STATE $sim=HI(obj\_model,pred\_model)$
+  %\STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
+  %\STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
+  \IF{$sim < f sim_{root}$}
+    \FOR{$i=1$ to $n.childNum$}
+      \STATE s\{i\}=SUBTRACTIVE\_PRUNE(n.children\{i\},$m_m$,
+      \STATE ...$sim_{root}$, $f$)
+    \ENDFOR
+    %\STATE SUBTRACTIVE\_PRUNE(n.children)
   \ELSE
@@
 \caption{SUBTRACTIVE\_PRUNE}
-\label{alg:sub_prun}
+\label{alg:sub_prune}
 \end{algorithm}
 
-The subtractive algorithm begins at the root of the tree and predicts attributes.
-This attribute distribution and its associated probability $P_{root}$ is assumed to be
-canonical for the image.  That is, any final segmentation should not have
-significantly less probability $P_{pred}$ than $P_{root}$.  The algorithm traverses
+The algorithm begins at the root of the tree and predicts attributes.
+This attribute distribution and its associated similarity $sim_{root}$
+to the object's canonical distribution is taken to be
+the standard for the image.  That is, any final segmentation should not have
+significantly less similarity $sim$ than $sim_{root}$.  The algorithm traverses
 the subtractive tree depth-first, predicting on each node.
-Any node that doesn't have a significant negative effect on the probability
-of the presence of the object is removed.  This test is done on line 9.  If the
-predicted probability was significantly affected, then we know that the region
-must remain.  But it doesn't mean that sub-regions might be able to be pruned
-out.  So the procedure is called recursively, checking for smaller regions
-that might be able to be pruned (line 10).
+Any node that doesn't have a significant negative effect on the similarity as
+compared to the standard is removed.  If the
+similarity was significantly affected, then we know that the region
+must remain.  But it doesn't mean that sub-regions might not be able to be pruned
+out, so the procedure is called recursively, checking for smaller regions
+that might be able to be pruned.
 
 If the probability was not significantly affected, then the mask is applied
-(line 12) and no recursive call is made.  This is important, because it means
+and no recursive call is made.  This is important, because it means
 that we can remove large chunks of the image wholesale and bypass predicting
@@
 \includegraphics[width=0.22\textwidth]{figures/parking_1.0.eps}
-}
-\caption{Result of adjusting the factor $f$ in the subtractive algorithm.
-\subref{fig:fa} shows running the algorithm with $f=0.9$ and \subref{fig:fb}
-shows running the algorithm with $f=1.0$.  Note that \subref{fig:fb} retains
-more of the cars, especially the two closest on the right and left, but also
-hsa more false-positive pixels, such as the ceiling region of the parking
-garage.}
+} \caption{Result of adjusting the factor $f$ in the subtractive
+algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
+and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
+that \subref{fig:fb} retains more of the cars, especially the two
+closest on the right and left, but also has more false-positive
+pixels, such as the ceiling region of the parking garage.}
 \label{fig:f}
@@
 \label{sec:results}
-Here are some results.
- trained using images from the pascal 
-2008 dataset using the same annotations used in \cite{farhadi09}.
+
+In this section, we evaluate our attribute based object detection
+and segmentation algorithm. We will answer four questions. (1) What
+is the performance of object detection and segmentation? (2) What is
+the influences of different parameters? (3) What are the advantages
+of the two pruning algorithms? (4) Is vertical confidence
+propagation useful? (In this draft, we only have partial results, so
+not all the questions are considered.)
+
+%\subsection{Dataset}
+%\label{ssec:dataset}
+
+We use the Pascal2008 dataset. This dataset has a lot of real life
+images which are more difficult to classify. The objects are labeled
+by bounding boxes not accurate segmentation. For training the
+attributes, we use the pascal2008 training set. The attribute
+annotations used in \cite{farhadi09} are freely available and we
+used them for training too. For testing the classification and
+segmentation, we use the pascal2008 validation set. We plan to do
+three classes classification and segmentation, including car,
+aeroplane and horse. Now we only got the results on car. We will
+incorporate the other classes in the final version.
+
+Table \ref{table:aresults} shows some of the results from running
+the additive algorithm on all cars in the dataset.  The recall is
+the rate of correctly detecting images with cars.  The segmentation
+precision is calculated with
+\[ V(M_{groundtruth},M_{pred}) = \frac{|M_{groundtruth} \cap M_{pred}|}{|M_{groundtruth} \cup M_{pred}|} \]
+where $M_{groundtruth}$ is the groundtruth mask calculated from the
+bounding boxes stored with the annotations and $M_{pred}$ is the
+predicted segmentation mask.  We of course recognize that the
+bounding boxes are not a good measure of segmentation truth, but
+it's the best we have available.
+
+The segmentation precision for the additive algorithm
+is far better than the precision for the subtractive algorithm (which averaged
+0.09).  This is because the additive algorithm only segments images for
+which it has predicted presence of a car, so that any image pruned by the
+algorithm already has a high car similarity score, enhancing the segmentation.
+The subtractive algorithm, on the other hand, assumes presence of a car in
+the image and proceeds no matter how poor the initial similarity score is.
+(For the final paper we expect to have results comparing the precision
+of the two algorithms based only on images segmented by both.)
+
+Figures \ref{fig:good_results} and \ref{fig:bad_results} show the
+results of segmentations of various images by both pruning
+algorithms. Figure \ref{fig:good_results} shows some good results,
+while Figure \ref{fig:bad_results} shows some bad results. This
+shows clear linkage between prominence of the side profile of the
+car and success of the segmentation. It appears that the attribute
+classifiers are more accurate on side profiles than front and rear
+shots, although rear shots performed reasonably well when tail
+lights were not illuminated.
+
+\begin{table}
+\centering
+\begin{tabular}{|l|l|l|}
+\hline Parameter & recall & prec \\
+\hline 0.8,0.4,0.1  & 0.4317 & 0.2393 \\
+\hline 0.8,0.4,0.15  & 0.3849 & 0.2370 \\
+\hline 0.8,0.6,0.15  & 0.2720 & 0.2501 \\
+\hline
+\end{tabular}
+\caption{Results from the additive algorithm on all car images.
+Parameter contains the three threshold, $thre\_perf$, $thre\_pos$
+and $thre\_neg$, recall is the object detection recall rate and prec
+is the segmentation precision on all detected images.}
+\label{table:aresults}
+\end{table}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:good_results}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
+Car not detected &
+\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:bad_results}
+\end{figure*}
 
@@
 %-------------------------------------------------------------------------------
-\section{Conclusions and future work}
-\label{sec:conclusions}
-Highly dependent on attribute selection and discriminatory ability of attributes.
+\section{Discussion}
+\label{sec:discussion}
+It can be seen that in simple cases both additive and subtractive algorithms
+are able to segment out rough outlines of the objects.  In most cases, even
+the more difficult ones, at least part of the car was present in the final
+segmentation.  This shows that the segmentation algorithms appear to be
+reasonable approximations to a combinatoric approach -- that of predicting
+on every combination of regions in the image.
+
+Despite these encouraging initial results, the final segmentation region
+was often not coherent.
+This appears to be largely because the region tree approach is not
+constrained by spatial coherence.  That is, two leaf nodes containing image
+regions that are spatially next to each other may be very distant in the
+region tree.  Because of this, the attribute distribution may change significantly
+after considering the first node and before consideration of the second node.
+Another reason for this may be that our canonical attribute distribution for
+our objects gave equal weights to each attribute.  For example, a wheel was
+equally as important as shininess.  This gave unfair disadvantages to
+under-represented or ill-trained attributes.  This can be seen in the results
+where the body of the car is removed while the wheels or headlights are
+retained.
+
+As object detection is generally only as good as the features used, so also it
+appears that this approach to segmentation is only as good as the attribute
+selection and training.  We found that in images with poor segmentations, the
+confidences in prediction of car attributes were generally low.  One problem
+with this implementation of attribute classifiers was that we didn't use
+the selection criterion described in \cite{farhadi09} that enhances within
+category prediction ability.  This means that, for example, the wheel attribute
+is highly similar to the car attribute and thus its discrimative ability
+is hurt.  One future direction for this research would be to improve the attribute
+training using the additional selection criterion and observe effects on
+the segmentations.
+
+An interesting orthogonal direction that could be taken with these ideas is to
+use segmentation using attributes as a diagnostic tool for attribute classifiers.
+That is, the segmentations produced by our algorithms can help zero in on areas
+in an image that exhibit high responses in detection of certain attributes.
+For example, an image could be segmented using similarity to a canonical distribution
+using only one attribute.  If that attribute is ``fur'' and segmentations
+consistently show paws and tails, then it would quickly become clear that
+the fur attribute classifier has learned on something other than fur.
+
+The holy grail of this approach, of course, is to be able to segment objects
+for which the canonical attribute distribution is unknown, based on a measure
+of attribute coherence.  If this can be achieved, then segmentation experiments
+could open up to non-experts, who could define coherence measures based on
+semantic attributes and then could use this approach to automatically segment large
+numbers of images even if no detection of their desired object exists.
+
+Another problem with the attribute based method is that the attributes are not discriminative 
+enough to separate different objects. For example, if we use the general attributes of head, torso and leg to 
+do the object classification, we cannot separate dog and cat, since both of them have all of the attributes. 
+But those attributes can definitely separate the two objects from non-animal objects, such as car. This example demonstrates that 
+attributes are helpful for the object classification, but they are not discriminative enough. So one way to deal with this is to use 
+both attributes features and low level objects features for object classification. We can train a general attributes models first. 
+When we want to classify some specific objects, we can incorporate a small number of low level features from the specific object samples to the attributes 
+features. In this way, we both reduce the training samples for object classification, and make the attribute based method more discriminative.
 

### 2010-05-01 grouping/hierarchy.m

@@ -90,6 +90,8 @@ attStruct.child={};
 attStruct.childNum=0;
 attStruct.attribute=attPred;
 attStruct.confidence=attConf;
+attStruct.mask=mask;
+attStruct.area=sum(sum(mask));
 
 if (size(label_vec, 1) > 1),
 

### 2010-05-01 test.m

@@ -199,6 +199,13 @@ if (TRAIN==1)
     att = attributes_train(:,i);
     att_pos=find(att==1);
     
+    rand('seed',1);
+
+    if length(att_pos)>500
+        rand_temp=randperm(length(att_pos));
+        att_pos=att_pos(rand_temp(1:500));
+    end
+    
     % change attributes mask
     %if length(att_pos)<att_train_thre
     %  atts_mask(i)=0;
@@ -206,8 +213,8 @@ if (TRAIN==1)
 
     att_neg=find(att==0);
     if ((length(att_neg)/length(att_pos))>((1-ratio)/ratio))
-        rand_temp=randperm(floor(length(att_pos)/ratio*(1-ratio)));
-        att_neg=att_neg(rand_temp);
+        rand_temp=randperm(length(att_neg));
+        att_neg=att_neg(rand_temp(1:floor(length(att_pos)/ratio*(1-ratio))));
     end
     if length(att_pos)==0
         features_temp=features_train;
@@ -382,15 +389,16 @@ if (SEGMENTATION)
   %temp = 'goat_12.jpg';
   %temp = 'bag_377.jpg';
 
-  image_set = 'ayahoo_test';
-  %image_set = 'apascal';
+  %image_set = 'ayahoo_test';
+  image_set = 'apascal';
   gPbdir = [BasePath,'out/',image_set,'_images/processed/gPb'];
   img_dir = [BasePath,'data/',image_set,'_images'];
   hog_dir = [BasePath,'out/',image_set,'_images/processed/hog'];
   tc_dir = [BasePath,'out/',image_set,'_images/processed/tc2'];
 
-  temp = 'monkey_220.jpg';
-  temp = 'monkey_221.jpg';
+  %temp = 'monkey_220.jpg';
+  %temp = 'monkey_221.jpg';
+  temp='2008_007214.jpg';
   
   %img_name = regexprep(char(names_test(1)), '\.jpg', '');
   %img_fn = fullfile(img_dir, char(names_test(1)));
@@ -405,15 +413,40 @@ if (SEGMENTATION)
   [img, ucm2, mask2] = gPb(img_fn, sprintf('out/%s_images/processed',image_set));
 
   base_name = regexprep(char(temp), '.jpg', '');
-  out_dir = [BasePath,'/out/',base_name];
+  out_dir = [BasePath,'out/',base_name];
[…]

### 2010-05-01 trunk/grouping/visitor.m
draft paper

@@ -43,12 +43,12 @@ att_sort=sort_idx(sort_value>0);
 atts(att_sort)
 sort_value(sort_value>0)
 
-base_name = regexprep(char(img_name), '.jpg', '');
-fid = fopen(sprintf('out/%s/atts%s.txt', base_name, path), 'w');
-atts_sorted = atts(att_sort);
-sort_value = sort_value(sort_value>0);
-for i=1:size(att_sort(:))
-  fprintf(fid, '%1.3f %s\n', sort_value(i), atts_sorted{i});
-end
-fclose(fid);
+% base_name = regexprep(char(img_name), '.jpg', '');
+% fid = fopen(sprintf('out/%s/atts%s.txt', base_name, path), 'w');
+% atts_sorted = atts(att_sort);
+% sort_value = sort_value(sort_value>0);
+% for i=1:size(att_sort(:))
+%   fprintf(fid, '%1.3f %s\n', sort_value(i), atts_sorted{i});
+% end
+% fclose(fid);
 

### 2010-05-05 paper.tex
committed

@@
 declare the combined region an accurate segmentation for that object.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
-\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
-\end{figure}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
+\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
+\end{figure}
+
 %-------------------------------------------------------------------------------
@@
 which an Ultrametric Contour Map (UCM) is constructed, which defines
-the region hierarchy. Some example of the hierarchy segmentation is
-shown in Figure \ref{fig:tree}.
+the region hierarchy.  The UCM is stored as a grayscale image with
+contours around the segmented regions.  These contours have intensities
+representative of the region's location in the hierarchy.  So to find
+the first branch in the tree, threshold the UCM image with a value
+$t$ where $t = max{I(x,y)}$ where $I(x,y)$ is the intensity at pixel
+location $(x,y)$.  The thresholded image can then be flood-filled into
+regions.  These regions correspond to the branches on either side of
+the root node in the segmentation tree.  The next level of the tree is
+found by thresholding the UCM at the next highest intensity and so on.
+Figure \ref{fig:ucm} shows an example UCM image and figure \ref{fig:tree}
+shows the hierarchy generated from that UCM.
 
-After the construction of hierarchy segmentation tree, we detect all
-the attributes in each node, including the intermediate node and
-leaf node. We use the output of SVM as the confidence (not binary),
+After the construction of segmentation tree, we detect all
+the attributes in each node, including the intermediate and
+leaf nodes. We use the output of SVM as the confidence (not binary),
 so each node can be represented by the confidence distribution of
-all attributes.
+all attributes.  These distributions are stored and later used in
+the additive pruning algorithm.  Unfortunately the subtractive algorithm
+requires runtime predictions, and thus cannot use this preprocessing
+step.
 
@@
 
-Our objective is to detect object and segment it out. In our
-hierarchy segmentation tree, the problem changes to how to select
+Our objective is to detect objects and segment them out. In our
+segmentation tree, the problem changes to how to select
 those nodes belong to the desired object. We estimate the
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\subfigure[]{
-\label{fig:treea}
+\includegraphics[width=0.30\textwidth]{figures/2008_000052_ucm.bmp.eps}
+\caption{A UCM image from which a segmentation tree is derived.}
+\label{fig:ucm}
+\end{figure}
+
+\begin{figure}
+\centering
+%\subfigure[]{
+%\label{fig:treea}
 \includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
-}
-\subfigure[]{
-\label{fig:treeb}
-\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
-}
-\caption{The two segmentation hierarchies used by the additive \subref{fig:treea}
-and subtractive \subref{fig:treeb} algorithms.  The additive hierarchy breaks the
-regions into smaller and smaller regions, while the subtractive hierarchy increases
-the size of the regions as smaller and smaller chunks are removed from the image.}
+%}
+%\subfigure[]{
+%\label{fig:treeb}
+%\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
+%}
+\caption{The segmentation hierarchy used by the additive
+and subtractive algorithms.  This tree was generated from the UCM
+in figure \ref{fig:ucm}.}
 \label{fig:tree}
-\end{figure*}
+\end{figure}
 
@@
 the object, the segmentation of the child node is more accurate than
-that of the parrent node. (3) Even if some node has high confidence
+that of the parent node. (3) Even if some node has high confidence
 of containing the object, its segmentation can still be improved by
@@
   \STATE \textbf{output:}
-  \STATE \hspace{3 mm} $m_m$
+  \STATE \hspace{3 mm} mask $m_m$
   \STATE
   \STATE $m_n$ := mask of $n$
-  \STATE $pred\_model$ := predict attributes on image($m_n \cap m_m$)
+  \STATE $r = m_{m} \cap \verb+~+ m_{n}$
+  \STATE $pred\_model$ := predict attributes on image($r$)
   \STATE $sim=HI(obj\_model,pred\_model)$
@@
   \ELSE
-    \STATE $m_m = m_m \cap m_n$
+    \STATE $m_m = m_m \cap \verb+~+ m_n$
   \ENDIF
@@
 significantly less similarity $sim$ than $sim_{root}$.  The algorithm traverses
-the subtractive tree depth-first, predicting on each node.
-Any node that doesn't have a significant negative effect on the similarity as
-compared to the standard is removed.  If the
-similarity was significantly affected, then we know that the region
-must remain.  But it doesn't mean that sub-regions might not be able to be pruned
+the subtractive tree depth-first.  At each node, attributes are predicted for 
+a region $r$.  
+$r$ is obtained by taking the intersection of the master mask and the inverted
+node mask ($r = m_{m} \cap \verb+~+ m_{n}$).  The intuition is this: the master mask is our current best guess at
+the region that contains an object.  By taking the intersection, we effectively
+subtract the node's region out.
+We can then predict on the new region.  If 
+there is no significant negative effect on the similarity as
+compared to the standard, then we assume that we can safely prune off the node's
+region without removing a part of the object..  If the
+similarity was significantly affected, then we assume that the region
+contains some part of the object and we allow it to remain.  But that 
+doesn't mean that sub-regions might not be able to be pruned
 out, so the procedure is called recursively, checking for smaller regions
@@
 
-If the probability was not significantly affected, then the mask is applied
+As mentioned, if the similarity score was not significantly affected by
+predicting on the master mask with the region removed, then the region is
+permanently removed from the master mask
 and no recursive call is made.  This is important, because it means
@@
 on the node's posterity.
+The runtime performance of the algorithm is dominated by the prediction step.
+Thus the advantage of pruning large chunks early is highly beneficial to
+the runtime of the algorithm.
 
@@
 
-The runtime performance of the algorithm is dominated by the prediction step.
-Thus the advantage of pruning large chunks early is highly beneficial to
-the runtime of the algorithm.
+The subtractive algorithm knows nothing about the number of objects present
+in the image.  It attempts to segment any object out into the final region.
+This is evident in figure \ref{fig:sub1}.  The mobile homes in the background
+have car attributes and thus are included in the final segmentation, even
+though they take a far less prominent role in the unsegmented image.  Another
+example is figure \ref{fig:truck}, where the two cars visually behind the truck
+are segmented alongside the truck.
 
@@
 \label{fig:f}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[]{
+\label{fig:sub1a}
+\includegraphics[width=0.22\textwidth]{figures/results/2008_000052.jpg.eps}
+}
+\subfigure[]{
+\label{fig:sub1b}
+\includegraphics[width=0.22\textwidth]{figures/2008_000052_1.00.jpg.eps}
+} \caption{Subtractive segmentation on an image with multiple objects.
+An observer may not even notice the trailer homes in the background in
+the original image \subref{fig:sub1a},
+but the segmentation includes a portion of them in the final segmentation \subref{fig:sub1b}.
+Subtractive segmentation attempts to segment all objects present
+in the image.}
+\label{fig:sub1}
 \end{figure}

### 2010-05-11 paper.tex
paper with results of add

@@
 \begin{tabular}{|l|l|l|}
-\hline Parameter & recall & prec \\
-\hline 0.8,0.4,0.1  & 0.4317 & 0.2393 \\
-\hline 0.8,0.4,0.15  & 0.3849 & 0.2370 \\
-\hline 0.8,0.6,0.15  & 0.2720 & 0.2501 \\
+\hline Methods & Precision(\%) & Recall(\%) \\
+\hline LowFea  & 55.97 & 70.96 \\
+\hline Att1    & 51.89 & 51.89 \\
+\hline Random  & 35.19 & 50.00 \\
+\hline Add     & 60.82 & 54.06 \\
 \hline
 \end{tabular}
-\caption{Results from the additive algorithm on all car images.
-Parameter contains the three threshold, $thre\_perf$, $thre\_pos$
-and $thre\_neg$, recall is the object detection recall rate and prec
-is the segmentation precision on all detected images.}
+\caption{Object classification results of three baseline methods and the proposed additive algorithm.}
 \label{table:aresults}
@@
 \label{fig:bad_results}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_007064.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_000052.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_007171.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_000251.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_007064.jpg_1_good.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_000052.jpg_1_good.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_007171.jpg_1_good.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_000251.jpg_1_good.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:good_results_car}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_000868.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_000884.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_001830.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_001867.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_000868.jpg_1_bad.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_000884.jpg_1_bad.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_001830.jpg_1_bad.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/car/2008_001867.jpg_1_bad.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:good_results_car}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:good_results_car}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:good_results_car}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:good_results_car}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
+\includegraphics[width=3.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:good_results_car}
 \end{figure*}

### 2010-05-11 trunk/paper.tex
changes

@@
 Our work focuses on leveraging attributes to produce accurate segmentations.
-The idea is to find image regions with salient attribute distributions.  If
-these regions can be combined together to for larger regions with attribute 
-distributions matching some object's canonical distribution then one can
+The idea is to find image regions with attribute distributions very similar
+to some canonical distribution for an object.  We define the ``canonical distribution''
+to be an attribute distribution representative of that object.  For example, the
+canonical distribution for a ``car'' would have some measure of ``shininess'', some
+other measure of ``window'' and so forth.  If
+regions can be combined together to for larger regions with attribute
+distributions matching the object's canonical distribution then one can
 declare the combined region an accurate segmentation for that object.
+
+We note that it is possible that one segmented region may contain the object and
+nothing else.  Though possible, in practice it is highly unlikely.  Even for rather
+simple objects, the true region of the object is distributed among various
+segmentations.  This is because all but the most trivial objects have different
+sub-regions of different colors, textures, contours, etc.  Thus we must search
+for a combination of these sub-regions that make up the object.
 
@@
 }
-\caption{Segmentation by maximizing attribute saliency.  \subref{fig:trucka} shows
+\caption{Segmentation by maximizing attribute similarity to a canonical
+attribute distribution for a car.  \subref{fig:trucka} shows
 the original image with any ``car'' attributes that were predicted.  $P$ is the probability
@@
 
-In practice, however, the testing of all combinations of regions to find 
-objects is intractable.  We use two approximatory algorithms operating on
-a segmentation hierarchy to determine salient regions.  Both are subtractive
-algorithms, which first predict attributes on the entire region and then
-proceed by observing the effects of removing different regions during
-a top-down traversal of the tree.  The benefit of using these methods are
-that large regions that clearly don't contribute to attribute saliency
-can be pruned from the tree early in the traversal.  This approach avoids
-the combinatoric complexity of a full search and, even more, prunes many
-regions from the segmentation tree before they even are searched, bringing
-the computational complexity, in practice, to roughly $O(n)$ where $n$ is
-the number of leaves in the segmentation tree.
+In general, the testing of all combinations of regions to
+find objects is intractable.  We use two approximatory algorithms
+operating on a segmentation hierarchy to determine regions belonging
+to a given class.
+One algorithm is additive and operates by combining regions that are likely
+to be part of the object.  The other is subtractive, which first predict attributes on
+the entire region and then proceeds by observing the effects of
+removing different regions during a top-down traversal of the tree.
+The benefit of using these methods are that large regions that
+clearly don't contribute to an attribute distribution similar to the
+canonical can be pruned from
+the tree early in the traversal.  This approach avoids the
+combinatoric complexity of a full search and, even more, prunes many
+regions from the segmentation tree before they even are searched,
+bringing the computational complexity, in practice, to roughly
+$O(n)$ where $n$ is the number of leaves in the segmentation tree.
+The flowchart of our algorithm is shown in Figure
+\ref{fig:flowchart}.
+
+This work is done using attributes as the features, but the segmentation
+pruning algorithms are actually feature-type agnostic and could be used
+with any image feature given a scoring function applicable to that feature.
 
@@
 that takes more advantage of attributes: that of segmenting \emph{unknown}
-objects from an image that exhibit salient but unrecognized attribute
+objects from an image that exhibit stable but unrecognized attribute
 distributions.  This type of application brings out some of the true power of
@@
 \label{sec:related_work}
-[Note: this section was lifted straight from our extended abstract
-and has not yet been updated to reflect what we actually did.]
-
 A significant amount of recent work has been done in the area of using
@@
 to the image and then refining the top-down segmentation using their
-segmentation hierarchy.  Our approach is very similar to this in spirit.
-While our initial estimate of segmentation is from the bottom-up (while
-theirs is from the top-down) we will use the hierarchical information
-from the segmentation to boost confidences of segmentation at the lowest
-level, similar to what they do.
+segmentation hierarchy.  Our approach doesn't use any confidence boosting based
+on the hierarchy like they do, but rather, the hierarchy is used to guide
+efficient removal and combination of regions.
 
-Another interesting work is that of Gould et al \cite{gould08}.  They use
-superpixels for an initial segmentation, build a CRF that includes a
-relative location feature in the energy function and minimizes the CRF
-for a final segmentation.  The relative location feature is determined
-using prior location probability maps.  Our approach is similar to this
-as well, in that we will also incorporate relative location information,
-although ours will use attributes' relative locations rather than object
-classes.  We will also use a CRF for the final segmentation, but will
-use a min-cut solution since our labels are binary.
-Kumar et al \cite{kumar05} incorporate shape structure into the segmentation by
-adding a latent shape parameter to the CRF.  This seems like it would be
-a useful addition to our system but make the scope too large.
+%Another interesting work is that of Gould et al \cite{gould08}.  They use
+%superpixels for an initial segmentation, build a CRF that includes a
+%relative location feature in the energy function and minimizes the CRF
+%for a final segmentation.  The relative location feature is determined
+%using prior location probability maps.  Our approach is similar to this
+%as well, in that we will also incorporate relative location information,
+%although ours will use attributes' relative locations rather than object
+%classes.  We will also use a CRF for the final segmentation, but will
+%use a min-cut solution since our labels are binary.
+%Kumar et al \cite{kumar05} incorporate shape structure into the segmentation by
+%adding a latent shape parameter to the CRF.  This seems like it would be
+%a useful addition to our system but make the scope too large.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
+\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
+\end{figure}
 
@@
 
-We use similar algorithm as \cite{farhadi09} to train the attribute models.
-Three different type of features are used, such as HOG, texture and color descriptors\cite{farhadi09}.
-Those features can capture different properties.
-We use kmeans to quantize all the features.
+We use a similar algorithm to that used in \cite{farhadi09} to train the attribute models.
+Three different type of features are used: HOG, texture and color descriptors \cite{farhadi09}.
+We use kmeans to quantize the features.
 The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively.
-All the quantized features are concatenated to form the 1384 deminsional feature.
+All quantized features are concatenated to form a 1384 dimensional feature.
+These low-level features are generated for training and testing datasets using the entire image.
+This is done to avoid introducing any feature artifacts as a result of black space surrounding segmented regions.
 
-For training, we use SVM classifier with Gaussian kernel to train model for each attribute. The precision of all the attributes on the test set is illustrated in figure?.
+For training, we use an SVM classifier with a Gaussian kernel to train
+the model for each attribute.
+
+%The precision of all the attributes on the test set is illustrated
+%in figure?.
 
@@
 
-We use the segmentation
-approach of \cite{arbelaez09}.  This produces a hierarchical
-segmentation by first detecting contours using the \emph{gPb} detector
-\cite{maire08}.  Once the contours are detected, regions are discovered using a
-watershed algorithm after which an Ultrametric Contour Map (UCM) is constructed,
-which defines the region hierarchy. Some example of the hierarchy segmentation is shown in figure?
+We use the segmentation approach of \cite{arbelaez09}.  This
+produces a hierarchical segmentation by first detecting contours
+using the \emph{gPb} detector \cite{maire08}.  This contour detector
+is advantageous because it uses brightness, color and texture
+gradients at multiple scales.  Once the contours are
+detected, regions are discovered using a watershed algorithm after
+which an Ultrametric Contour Map (UCM) is constructed, which defines
+the region hierarchy.  The UCM is stored as a grayscale image with
+contours around the segmented regions.  These contours have intensities
+representative of the region's location in the hierarchy.  So to find
+the first branch in the tree, threshold the UCM image with a value
+$t$ where $t = max{I(x,y)}$ where $I(x,y)$ is the intensity at pixel
+location $(x,y)$.  The thresholded image can then be flood-filled into
+regions.  These regions correspond to the branches on either side of
+the root node in the segmentation tree.  The next level of the tree is
+found by thresholding the two new regions of the UCM at each, respective,
+next highest intensity and so on.
+Figure \ref{fig:ucm} shows an example UCM image and figure \ref{fig:tree}
+shows the hierarchy generated from that UCM.
 
-After the construction of hierarchy segmentation tree, we detect all the attributes in each node, including the intermedia node and leaf node.
-We use the output of SVM as the confidence (not binary), so each node can be represented by the confidence distribution of all attributes.
+After the construction of segmentation tree, we detect all
+the attributes in each node, including the intermediate and
+leaf nodes. We use the output of SVM as the confidence (not binary),
+so each node can be represented by the confidence distribution of
+all attributes.  These distributions are stored and later used in
+the additive pruning algorithm.  Unfortunately the subtractive algorithm
+requires runtime predictions, and thus cannot use this preprocessing
+step.
 
@@
 
-Our objective is to detect object and segment it out.
-In our hierarchy segmentation tree, the problem changes to how to select those nodes belong to the desired object.
-We estimate the probability that a node is belong to object based on the attribute confidence distribution.
-For each object, we manually give the desired attribute distribution by common knowledge.
-We use the histogram intersection between the desired distribution and the estimated confidence distribution in each node as the similarity measure.
-The histogram intersection is calculated as follows:
+Our objective is to detect objects and segment them out. Using a segmentation tree
+we cast the problem into one of selecting nodes that belong 
+to the desired object. We estimate the
+probability that a node belongs to object based on the attribute
+confidence distribution. For each object, we manually determine a
+canonical attribute distribution.  We use the
+histogram intersection between the desired distribution and the
+estimated confidence distribution in each node as the similarity
+measure. The histogram intersection is calculated as follows:
 
-\[ HI(H_{model},H_{pred}) = \frac{|H_{model} \cap H_{pred}|}{|H_{model}|} \]
+\[ HI(H_{model},H_{pred}) = \frac{|H_{model} \cap H_{pred}|}{|H_{model}|}
+\] ,
 
-To select the nodes, we propose two different top-down prune algorithms, additive algorithm and subtractive algorithm.
-We use the UCM to generate two types of region tree, shown in figure \ref{fig:tree}.
-The first tree is an additive tree, where regions are subdivided into successively
-smaller regions moving down in the tree.  We call it ``additive'' because the
-original image can be reconstructed by adding the regions from each leaf node
-together.  The figures show the nodes of the trees as containing images, but in
-truth the trees contain binary masks which, when applied to the original image,
-produce the shown node contents.
+where $H_{model}$ and $H_{pred}$ represent the desired attribute
+distribution and predicted distribution.
 
-The second tree is ``subtractive.''  The tree has identical structure to the additive
-tree and each node contains the inverse of the mask of the corresponding node
-in the additive tree.
+To select the nodes, we use two different top-down pruning algorithms, 
+the ``additive'' algorithm and the ``subtractive'' algorithm. 
+Each of these algorithms prunes the region tree until a final segmentation
+meeting some criterion of absolute or relative attribute similarity to the canonical is found.
+We now discuss each algorithm in detail.
 
-The final segmentation is obtained by pruning the region tree until a final segmentation
-meeting some criterion of absolute or relative attribute saliency is found.
-We have two methods for pruning the tree, each showing relative strengths and
-weakness.  The first is a semi-greedy additive approach which uses the additive
-tree.  The second is a greedy subtractive approach.  We now discuss each of these 
-in detail.
+\begin{figure}
+\centering
+\includegraphics[width=0.30\textwidth]{figures/2008_000052_ucm.bmp.eps}
+\caption{A UCM image from which a segmentation tree is derived.}
+\label{fig:ucm}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
 \centering
-\subfigure[]{
-\label{fig:treea}
+%\subfigure[]{
+%\label{fig:treea}
 \includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
-}
-\subfigure[]{
-\label{fig:treeb}
-\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
-}
-\caption{The two segmentation hierarchies used by the additive \subref{fig:treea}
-and subtractive \subref{fig:treeb} algorithms.  The additive hierarchy breaks the
-regions into smaller and smaller regions, while the subtractive hierarchy increases
-the size of the regions as smaller and smaller chunks are removed from the image.}
+%}
+%\subfigure[]{
+%\label{fig:treeb}
+%\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
+%}
+\caption{The segmentation hierarchy used by the additive
+and subtractive algorithms.  This tree was generated from the UCM
+in figure \ref{fig:ucm}.}
 \label{fig:tree}
-\end{figure*}
+\end{figure}
 
@@
 
-This pruning algorithm is based on three observations.
-(1) At least one node in the segmentation tree contrains the whole object.
-(This is always true since the root node contains the whole image).
-(2) If both parent node and child node have high confidence of containing the object, the segmentation of the child node is more accurate than that of the parrent node.
-(3) Even if the same node has high confidence of containing the object, its segmentation can still improve.
-The details of the additive algorithm is shown in algorithm \ref{alg:add_prune}.
+This pruning algorithm is based on three observations. (1) At least
+one node in the segmentation tree contrains the whole object. (This
+is always true since the root node contains the whole image). (2) If
+both parent node and child node have high confidence of containing
+the object, the segmentation of the child node is more accurate than
+that of the parent node. (3) Even if some node has high confidence
+of containing the object, its segmentation can still be improved by
+removing irrelevant children node. The details of the additive
+algorithm is shown in algorithm \ref{alg:add_prune}.
 
-The idea of the algorithm is to find the smallest discriminative regions, either positive or negative, and combine all of them together to form the final segmentation.
-We use three threshold for the similarity measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent perfect segment, positive segment and negative segment, respectively.
-If the similarity is above $thre\_perf$, which means the segmentation is perfect, we cut all the nodes below and return this segment.
-If the similarity is below $thre\_neg$, which means the segment does not contain the object, we cut all the nodes below and return NULL.
-If the similarity is between $thre\_perf$ and $thre\_pos$, which means the node definitely contains the object but the segmentation is not perfect yet, we keep on checking its children nodes to refine the segmentation.
-The final case is that the similarity is between $thre\_pos$ and $thre\_neg$, which means we are not sure whether there is an object in the node, so we just keep on searching its children.
+The idea of the algorithm is to find the smallest discriminative
+regions, either positive or negative. We combine all the smallest
+positive regions while remove all the negative ones to form the
+final segmentation. We use three threshold for the similarity
+measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent
+perfect segment, positive segment and negative segment,
+respectively. If the similarity is above $thre\_perf$, which means
+the segmentation is perfect for the object, we cut all the nodes
+below and return this segment. If the similarity is below
+$thre\_neg$, which means the segment does not contain the object, we
+cut all the nodes below and return NULL. If the similarity is
+between $thre\_perf$ and $thre\_pos$, which means the node
+definitely contains the object but the segmentation is not perfect
+yet, we keep on checking its children nodes to refine the
+segmentation. The final case is that the similarity is between
+$thre\_pos$ and $thre\_neg$, which means we are not sure whether
+there is an object in the node, so we just keep on searching its
+children.
 
@@
   \STATE \hspace{3 mm} factor $f$
+  \STATE \textbf{output:}
+  \STATE \hspace{3 mm} mask $m_m$
+  \STATE
   \STATE $m_n$ := mask of $n$
-  \STATE $pred\_model$ := predict attributes on image($m_n \cap m_m$)
+  \STATE $r = m_{m} \cap \verb+~+ m_{n}$
+  \STATE $pred\_model$ := predict attributes on image($r$)
   \STATE $sim=HI(obj\_model,pred\_model)$
@@
 significantly less similarity $sim$ than $sim_{root}$.  The algorithm traverses
-the subtractive tree depth-first, predicting on each node.  
-Any node that doesn't have a significant negative effect on the similarity as 
-compared to the standard is removed.  If the
-similarity was significantly affected, then we know that the region
-must remain.  But it doesn't mean that sub-regions might not be able to be pruned
+the subtractive tree depth-first.  At each node, attributes are predicted for 
+a region $r$.  
+$r$ is obtained by taking the intersection of the master mask and the inverted
+node mask ($r = m_{m} \cap \verb+~+ m_{n}$).  The intuition is this: the master mask is our current best guess at
+the region that contains an object.  By taking the intersection, we effectively
+subtract the node's region out.
+We can then predict on the new region.  If 
+there is no significant negative effect on the similarity as
+compared to the standard, then we assume that we can safely prune off the node's
+region without removing a part of the object..  If the
+similarity was significantly affected, then we assume that the region
+contains some part of the object and we allow it to remain.  But that 
+doesn't mean that sub-regions might not be able to be pruned
 out, so the procedure is called recursively, checking for smaller regions
@@
 
-The runtime performance of the algorithm is dominated by the prediction step.
-Thus the advantage of pruning large chunks early is highly beneficial to 
-the runtime of the algorithm.
+The subtractive algorithm knows nothing about the number of objects present
+in the image.  It attempts to segment any object out into the final region.
+This is evident in figure \ref{fig:sub1}.  The mobile homes in the background
+have car attributes and thus are included in the final segmentation, even
+though they take a far less prominent role in the unsegmented image.  Another
+example is figure \ref{fig:truck}, where the two cars visually behind the truck
+are segmented alongside the truck.
 
@@
 \includegraphics[width=0.22\textwidth]{figures/parking_1.0.eps}
+} \caption{Result of adjusting the factor $f$ in the subtractive
+algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
+and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
+that \subref{fig:fb} retains more of the cars, especially the two
+closest on the right and left, but also has more false-positive
+pixels, such as the ceiling region of the parking garage.}
+\label{fig:f}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[]{
+\label{fig:sub1a}
+\includegraphics[width=0.22\textwidth]{figures/results/2008_000052.jpg.eps}
 }
-\caption{Result of adjusting the factor $f$ in the subtractive algorithm.
-\subref{fig:fa} shows running the algorithm with $f=0.9$ and \subref{fig:fb}
-shows running the algorithm with $f=1.0$.  Note that \subref{fig:fb} retains
-more of the cars, especially the two closest on the right and left, but also
-hsa more false-positive pixels, such as the ceiling region of the parking
-garage.}
-\label{fig:f}
+\subfigure[]{
+\label{fig:sub1b}
+\includegraphics[width=0.22\textwidth]{figures/2008_000052_1.00.jpg.eps}
+} \caption{Subtractive segmentation on an image with multiple objects.
+An observer may not even notice the trailer homes in the background in
+the original image \subref{fig:sub1a},
+but the segmentation includes a portion of them in the final segmentation \subref{fig:sub1b}.
+Subtractive segmentation attempts to segment all objects present
+in the image.}
+\label{fig:sub1}
 \end{figure}
@@
 
-In this section, we evaluate our attribute based object detection and segmentation algorithm.
-We will answer four questions.
-(1) What is the performance of object detection and segmentation?
-(2) What is the influences of different parameters?
-(3) What are the advantages of the two pruning algorithms?
-(4) Is vertical confidence propogation useful?
+In this section, we evaluate our attribute based object detection
+and segmentation algorithm. We will answer four questions. (1) What
+is the performance of object detection and segmentation? (2) What are
+the influences of different parameters? (3) What are the advantages
+of the two pruning algorithms? (4) Is vertical confidence
+propagation useful? (In this draft, we only have partial results, so
+not all the questions are considered.)
 
@@
 
-We use the Pascal2008 dataset.  The attribute annotations used in \cite{farhadi09}
-are freely available and we used them for training the attributes.
+We use the Pascal2008 dataset. This dataset has a lot of real life
+images which are more difficult to classify. The objects are labeled
+by bounding boxes not accurate segmentation. For training the
+attributes, we use the pascal2008 training set. The attribute
+annotations used in \cite{farhadi09} are freely available and we
+used them for training too. For testing the classification and
+segmentation, we use the pascal2008 validation set. We plan to do
+three classes classification and segmentation, including car,
+aeroplane and horse. Now we only got the results on car. We will
+incorporate the other classes in the final version.
 
-\ref{table:aresults} shows some of the results from running the additive algorithm
-on all cars in the dataset.  The recall is the rate of correctly detecting
-images with cars.  The segmentation precision is calculated with
-\[ V(M_{model},M_{pred}) = \frac{|M_{model} \cap M_{pred}|}{|M_{model} \cup M_{pred}|} \]
-where $M_{model}$ is the model mask calculated from the bounding boxes
-stored with the annotations and $M_{pred}$ is the predicted segmentation
-mask.  We of course recognize that the bounding boxes are not a good measure
-of segmentation truth, but it's the best we have available.
+Table \ref{table:aresults} shows some of the results from running
+the additive algorithm on all cars in the dataset.  The recall is
+the rate of correctly detecting images with cars.  The segmentation
+precision is calculated with
+\[ V(M_{groundtruth},M_{pred}) = \frac{|M_{groundtruth} \cap M_{pred}|}{|M_{groundtruth} \cup M_{pred}|} \]
+where $M_{groundtruth}$ is the groundtruth mask calculated from the
+bounding boxes stored with the annotations and $M_{pred}$ is the
+predicted segmentation mask.  We of course recognize that the
+bounding boxes are not a good measure of segmentation truth, but
+it's the best we have available.
 
@@
 
-Figures \ref{fig:good_results} and \ref{fig:bad_results} show the results
-of segmentations of various images by both images.  This shows clear linkage
-between prominence of the side profile of the car and success of the segmentation.
-It appears that the attribute classifiers are more accurate on side profiles
-than front and rear shots, although rear shots performed reasonably well when
-tail lights were not illuminated.
+Figures \ref{fig:good_results} and \ref{fig:bad_results} show the
+results of segmentations of various images by both pruning
+algorithms. Figure \ref{fig:good_results} shows some good results,
+while Figure \ref{fig:bad_results} shows some bad results. This
+shows clear linkage between prominence of the side profile of the
+car and success of the segmentation. It appears that the attribute
+classifiers are more accurate on side profiles than front and rear
+shots, although rear shots performed reasonably well when tail
+lights were not illuminated.
 
@@
 \centering
-\begin{tabular}{|l|l|l|l|}
+\begin{tabular}{|l|l|l|}
+\hline Methods & Precision(\%) & Recall(\%) \\
+\hline LowFea  & 55.97 & 70.96 \\
+\hline Att1    & 51.89 & 51.89 \\
+\hline Random  & 35.19 & 50.00 \\
+\hline Add     & 60.82 & 54.06 \\
 \hline
-$P$ & $D$ & recall & prec \\ \hline
-4, 1 & 227 & 0.4317 & 0.2393 \\ \hline
-4, 1.5 & 239 & 0.3849 & 0.2370 \\ \hline
-6, 1.5 & 239 & 0.2720 & 0.2501 \\ \hline
 \end{tabular}
-\caption{Results from the additive algorithm on all car images.  $P$ is
-the parameters, $D$ is the number of detections, recall is the detection
-recall rate and prec is the segmentation precision on all detected
-images.}
+\caption{Object classification results of three baseline methods and the proposed additive algorithm.}
 \label{table:aresults}
@@
 
+Another problem with the attribute based method is that the attributes are not discriminative 
+enough to separate different objects. For example, if we use the general attributes of head, torso and leg to 
+do the object classification, we cannot separate dog and cat, since both of them have all of the attributes. 
+But those attributes can definitely separate the two objects from non-animal objects, such as car. This example demonstrates that 
+attributes are helpful for the object classification, but they are not discriminative enough. So one way to deal with this is to use 
+both attributes features and low level objects features for object classification. We can train a general attributes models first. 
+When we want to classify some specific objects, we can incorporate a small number of low level features from the specific object samples to the attributes 
+features. In this way, we both reduce the training samples for object classification, and make the attribute based method more discriminative.
+
 \subsection*{Acknowledgements}

### 2010-05-11 trunk/paper.tex
updated paper

@@
 
-\title{Segmentation Using Attributes}
+\title{Attributes-based Object Classification and Segmentation}
 
-\author{Aibo Tian\\
+\author{Aibo Tian and John Edwards\\
+University of Texas at Austin\\
 %Institution1\\
 %Institution1 address\\
-{\tt\small atian@cs.utexas.edu}
+{\tt\small \{atian,edwardsj\}@cs.utexas.edu}
 % For a paper whose authors are all at the same institution,
@@
 % To save space, use either the email address or home page, not both
-\and
-John Edwards\\
+%\and
+%John Edwards\\
 %Institution2\\
 %First line of institution2 address\\
-{\tt\small edwardsj@cs.utexas.edu}
+%{\tt\small edwardsj@cs.utexas.edu}
+%University of Texas at Austin\\
 }
+%University of Texas at Austin\\
 
@@
 \label{sec:related_work}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
+\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
+\end{figure}
+
 A significant amount of recent work has been done in the area of using
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
-\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
+%\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
+%\end{figure}
 
@@
 Attributes are high-level features which can reflect semantic properties of objects.
-Given the attributes, we can do object detection based on the their distribution.
+Given the attributes, we can do object detection based on their distribution.
 We use the same attribute set as \cite{farhadi09}.
@@
 
-In this section, we evaluate our attribute based object detection
-and segmentation algorithm. We will answer four questions. (1) What
-is the performance of object detection and segmentation? (2) What are
-the influences of different parameters? (3) What are the advantages
-of the two pruning algorithms? (4) Is vertical confidence
-propagation useful? (In this draft, we only have partial results, so
-not all the questions are considered.)
+In this section, we evaluate our attribute based object classification
+and segmentation algorithm. We will also analyse the advantages and disadvantages of out algorithm.\\
 
-%\subsection{Dataset}
-%\label{ssec:dataset}
+\subsection{Dataset}
+\label{ssec:dataset}
 
-We use the Pascal2008 dataset. This dataset has a lot of real life
+We use the Pascal2008 dataset for both training and testing. This dataset has a lot of real life
 images which are more difficult to classify. The objects are labeled
@@
 used them for training too. For testing the classification and
-segmentation, we use the pascal2008 validation set. We plan to do
-three classes classification and segmentation, including car,
-aeroplane and horse. Now we only got the results on car. We will
-incorporate the other classes in the final version.
+segmentation, we use the pascal2008 validation set. Three classes are used in this experiment, including car,
+aeroplane and horse. We get 328 testing images, with car 150, aeroplane 103 and horse 93. Note that one image 
+can contain multiple objects in multiple classes.\\
 
-Table \ref{table:aresults} shows some of the results from running
-the additive algorithm on all cars in the dataset.  The recall is
-the rate of correctly detecting images with cars.  The segmentation
+\subsection{Measure}
+\label{ssec:measure}
+
+For object classification, we use precision and recall to measure the performance. 
+For segmentation, we use the ratio of intersection and union of the prediction and 
+groundtruth as the measure of precision. The segmentation
 precision is calculated with
@@
 bounding boxes are not a good measure of segmentation truth, but
-it's the best we have available.
+it's the best we have available.\\
 
-The segmentation precision for the additive algorithm
-is far better than the precision for the subtractive algorithm (which averaged
-0.09).  This is because the additive algorithm only segments images for
-which it has predicted presence of a car, so that any image pruned by the
-algorithm already has a high car similarity score, enhancing the segmentation.
-The subtractive algorithm, on the other hand, assumes presence of a car in
-the image and proceeds no matter how poor the initial similarity score is.
-(For the final paper we expect to have results comparing the precision
-of the two algorithms based only on images segmented by both.)
+\subsection{Classification}
+\label{ssec:classification}
 
-Figures \ref{fig:good_results} and \ref{fig:bad_results} show the
-results of segmentations of various images by both pruning
-algorithms. Figure \ref{fig:good_results} shows some good results,
-while Figure \ref{fig:bad_results} shows some bad results. This
-shows clear linkage between prominence of the side profile of the
-car and success of the segmentation. It appears that the attribute
-classifiers are more accurate on side profiles than front and rear
-shots, although rear shots performed reasonably well when tail
-lights were not illuminated.
+Table \ref{table:aresults} shows the classification results comparing the proposed method with 
+the other three baseline methods. LowFea means that we use the low level feature to train and test 
+the object classification directly. Att1 means that we use the attribute distribution as the feature,
+but we only test it in the whole image without segmentation. Random means random prediction. Add is our
+proposed algorithm with additive pruning. The proposed algorithm has the highest precision comparing 
+with the other baselines, while the recall is a little lower than LowFea. Figure \ref{fig:roc_class} 
+shows the ROC curve for each class and the average.\\
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/add_res/roc_class.png.eps}
+\caption{Result of adjusting the factor $f$ in the subtractive
+algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
+and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
+that \subref{fig:fb} retains more of the cars, especially the two
+closest on the right and left, but also has more false-positive
+pixels, such as the ceiling region of the parking garage.}
+\label{fig:roc_class}
+\end{figure}
+
+\subsection{Segmentation}
+\label{ssec:segmentation}
+
+Figure \ref{fig:roc_seg} shows the segmentation precision of additive pruning 
+versus the false positive rate of object classification. The segmentation precision
+is in the range of $20\%$ to $50\%$. Some of the segmentation results are shown in 
+Figure \ref{fig:car_good_results},\ref{fig:car_bad_results},\ref{fig:aeroplane_good_results},\ref{fig:aeroplane_bad_results},\ref{fig:horse_good_results},\ref{fig:horse_bad_results}.\\
+
+Figures \ref{fig:car_good_results} and \ref{fig:car_bad_results} show the
+segmentations of car images by both additive and subtractive pruning
+algorithms. Figure \ref{fig:good_results} shows some good results,
+while Figure \ref{fig:bad_results} shows some bad results. This
+shows clear linkage between prominence of the side profile of the
+car and success of the segmentation. It appears that the attribute
+classifiers are more accurate on side profiles than front and rear
+shots, although rear shots performed reasonably well when tail
+lights were not illuminated.\\
+
+Figures \ref{fig:aeroplane_good_results}, \ref{fig:aeroplane_bad_results} and 
+\ref{fig:horse_good_results}, \ref{fig:horse_bad_results} show some good and bad 
+segmentation results of additive algorithm on aeroplane and horse classes. Because of the
+high complexity of the subtractive algorithm, we did not run it on these two classes. The good 
+results are accurate to segment out the objects. One important note is that our algorithm can segment out
+multiple objects at the same time. The bad segmentations either miss 
+part of the object or contain so much background. The bad ones are caused 
+by two reasons. First, the hierarchical segmentation tree is not fine enough. We did not use all 
+levels in the segmentation tree. The more levels we use, the more time we need to spend on it. 
+Also when the segments are too small, the attribute detection is nearly random, because the small regions 
+do not have enough points to represent their properties. Second, the training of attributes based on
+bounding boxes is not accurate, because of many background pixels can be included in the bounding boxes. 
+This is especially obvious to the horse images, since horses are not convex enough in the images. 
+All the segmented images in figure \ref{fig:horse_bad_results} contains grass or trees, especially the 
+left one which only contains grass. These images prove that the grass or trees models are actually
+included in the horse model.\\
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/add_res/roc_seg.png.eps}
+\caption{Result of adjusting the factor $f$ in the subtractive
+algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
+and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
+that \subref{fig:fb} retains more of the cars, especially the two
+closest on the right and left, but also has more false-positive
+pixels, such as the ceiling region of the parking garage.}
+\label{fig:roc_seg}
+\end{figure}
+
+%\begin{figure*}[p]
+%\centering
+%\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+%\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
+%\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
+%\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
+%\end{tabular}
+%\caption{Selected results from segmentation of cars from the Pascal2008
+%dataset.  The first row shows the original image.  The second row shows
+%the best segmentation from the additive algorithm.  The third row shows
+%the segmentation from the subtractive algorithm with $f=0.9$.}
+%\label{fig:good_results}
+%\end{figure*}
+
+%\begin{figure*}[p]
+%\centering
+%\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+%\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
+%\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
+%Car not detected &
+%\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
+%\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
+%\end{tabular}
+%\caption{Selected results from segmentation of cars from the Pascal2008
+%dataset.  The first row shows the original image.  The second row shows
+%the best segmentation from the additive algorithm.  The third row shows
+%the segmentation from the subtractive algorithm with $f=0.9$.}
+%\label{fig:bad_results}
+%\end{figure*}
+
 \begin{figure*}[p]
 \centering
-\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
-\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_007064.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_000052.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_007171.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_000251.jpg.eps} \\
+
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_007064.jpg_1_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_000052.jpg_1_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_007171.jpg_1_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_000251.jpg_1_good.jpg.eps} \\
+
+\includegraphics[width=2.95cm]{figures/sub_results/2008_007064_1_bad_sub.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/sub_results/2008_000052_1_bad_sub.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/sub_results/2008_007171_1_bad_sub.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/sub_results/2008_000251_1_bad_sub.jpg.eps} \\
 \end{tabular}
@@
 the segmentation from the subtractive algorithm with $f=0.9$.}
-\label{fig:good_results}
+\label{fig:car_good_results}
 \end{figure*}
@@
 \centering
-\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
-\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
-%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
-Car not detected &
-\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_001961.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_003132.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004312.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004414.jpg.eps} \\
+
+\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_001961.jpg_1_bad.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_003132.jpg_1_bad.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004312.jpg_1_bad.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004414.jpg_1_bad.jpg.eps} \\
+
+\includegraphics[width=2.95cm]{figures/sub_results/good/2008_001961_0.80.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/sub_results/good/2008_003132_1.10.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/sub_results/good/2008_004312_1.00.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/sub_results/good/2008_004414_0.90.jpg.eps} \\
+
 \end{tabular}
@@
 the segmentation from the subtractive algorithm with $f=0.9$.}
-\label{fig:bad_results}
+\label{fig:car_bad_results}
 \end{figure*}
@@
 \centering
-\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_007064.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_000052.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_007171.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_000251.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_007064.jpg_1_good.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_000052.jpg_1_good.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_007171.jpg_1_good.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_000251.jpg_1_good.jpg.eps} \\
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
 \end{tabular}
@@
 the segmentation from the subtractive algorithm with $f=0.9$.}
-\label{fig:good_results_car}
+\label{fig:aeroplane_good_results}
 \end{figure*}
@@
 \centering
-\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_000868.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_000884.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_001830.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_001867.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_000868.jpg_1_bad.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_000884.jpg_1_bad.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_001830.jpg_1_bad.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/car/2008_001867.jpg_1_bad.jpg.eps} \\
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
 \end{tabular}
@@
 the segmentation from the subtractive algorithm with $f=0.9$.}
-\label{fig:good_results_car}
+\label{fig:aeroplane_bad_results}
 \end{figure*}
@@
 \centering
-\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
 \end{tabular}
@@
 the segmentation from the subtractive algorithm with $f=0.9$.}
-\label{fig:good_results_car}
+\label{fig:horse_good_results}
 \end{figure*}
@@
 \centering
-\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
 \end{tabular}
@@
 the segmentation from the subtractive algorithm with $f=0.9$.}
-\label{fig:good_results_car}
-\end{figure*}
-
-\begin{figure*}[p]
-\centering
-\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
-\end{tabular}
-\caption{Selected results from segmentation of cars from the Pascal2008
-dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f=0.9$.}
-\label{fig:good_results_car}
-\end{figure*}
-
-\begin{figure*}[p]
-\centering
-\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
-\end{tabular}
-\caption{Selected results from segmentation of cars from the Pascal2008
-dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f=0.9$.}
-\label{fig:good_results_car}
+\label{fig:horse_bad_results}
 \end{figure*}

### 2010-05-12 paper.tex
changes

--- 2010-05-05 paper.tex
@@
 Our work focuses on leveraging attributes to produce accurate segmentations.
-The idea is to find image regions with salient attribute distributions.  If
-these regions can be combined together to for larger regions with attribute
-distributions matching some object's canonical distribution then one can
+The idea is to find image regions with attribute distributions very similar
+to some canonical distribution for an object.  We define the ``canonical distribution''
+to be an attribute distribution representative of that object.  For example, the
+canonical distribution for a ``car'' would have some measure of ``shininess'', some
+other measure of ``window'' and so forth.  If
+regions can be combined together to for larger regions with attribute
+distributions matching the object's canonical distribution then one can
 declare the combined region an accurate segmentation for that object.
+
+We note that it is possible that one segmented region may contain the object and
+nothing else.  Though possible, in practice it is highly unlikely.  Even for rather
+simple objects, the true region of the object is distributed among various
+segmentations.  This is because all but the most trivial objects have different
+sub-regions of different colors, textures, contours, etc.  Thus we must search
+for a combination of these sub-regions that make up the object.
 
@@
 
-In practice, however, the testing of all combinations of regions to
+In general, the testing of all combinations of regions to
 find objects is intractable.  We use two approximatory algorithms
-operating on a segmentation hierarchy to determine salient regions.
-Both are subtractive algorithms, which first predict attributes on
-the entire region and then proceed by observing the effects of
+operating on a segmentation hierarchy to determine regions belonging
+to a given class.
+One algorithm is additive and operates by combining regions that are likely
+to be part of the object.  The other is subtractive, which first predict attributes on
+the entire region and then proceeds by observing the effects of
 removing different regions during a top-down traversal of the tree.
 The benefit of using these methods are that large regions that
-clearly don't contribute to attribute saliency can be pruned from
+clearly don't contribute to an attribute distribution similar to the
+canonical can be pruned from
 the tree early in the traversal.  This approach avoids the
@@
 
+This work is done using attributes as the features, but the segmentation
+pruning algorithms are actually feature-type agnostic and could be used
+with any image feature given a scoring function applicable to that feature.
+
 While we focus on segmentation of known objects, we anticipate an application
 that takes more advantage of attributes: that of segmenting \emph{unknown}
-objects from an image that exhibit salient but unrecognized attribute
+objects from an image that exhibit stable but unrecognized attribute
 distributions.  This type of application brings out some of the true power of
@@
 \label{sec:related_work}
-[Note: this section was lifted straight from our extended abstract
-and has not yet been updated to reflect what we actually did.]
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
+\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
+\end{figure}
 
@@
 to the image and then refining the top-down segmentation using their
-segmentation hierarchy.  Our approach is very similar to this in spirit.
-While our initial estimate of segmentation is from the bottom-up (while
-theirs is from the top-down) we will use the hierarchical information
-from the segmentation to boost confidences of segmentation at the lowest
-level, similar to what they do.
+segmentation hierarchy.  Our approach doesn't use any confidence boosting based
+on the hierarchy like they do, but rather, the hierarchy is used to guide
+efficient removal and combination of regions.
 
-Another interesting work is that of Gould et al \cite{gould08}.  They use
-superpixels for an initial segmentation, build a CRF that includes a
-relative location feature in the energy function and minimizes the CRF
-for a final segmentation.  The relative location feature is determined
-using prior location probability maps.  Our approach is similar to this
-as well, in that we will also incorporate relative location information,
-although ours will use attributes' relative locations rather than object
-classes.  We will also use a CRF for the final segmentation, but will
-use a min-cut solution since our labels are binary.
-Kumar et al \cite{kumar05} incorporate shape structure into the segmentation by
-adding a latent shape parameter to the CRF.  This seems like it would be
-a useful addition to our system but make the scope too large.
+%Another interesting work is that of Gould et al \cite{gould08}.  They use
+%superpixels for an initial segmentation, build a CRF that includes a
+%relative location feature in the energy function and minimizes the CRF
+%for a final segmentation.  The relative location feature is determined
+%using prior location probability maps.  Our approach is similar to this
+%as well, in that we will also incorporate relative location information,
+%although ours will use attributes' relative locations rather than object
+%classes.  We will also use a CRF for the final segmentation, but will
+%use a min-cut solution since our labels are binary.
+%Kumar et al \cite{kumar05} incorporate shape structure into the segmentation by
+%adding a latent shape parameter to the CRF.  This seems like it would be
+%a useful addition to our system but make the scope too large.
 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
-\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
+%\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
+%\end{figure}
 
@@
 
-We use similar algorithm as \cite{farhadi09} to train the attribute models.
-Three different type of features are used, such as HOG, texture and color descriptors\cite{farhadi09}.
-Those features can capture different properties.
-We use kmeans to quantize all the features.
+We use a similar algorithm to that used in \cite{farhadi09} to train the attribute models.
+Three different type of features are used: HOG, texture and color descriptors \cite{farhadi09}.
+We use kmeans to quantize the features.
 The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively.
-All the quantized features are concatenated to form the 1384 deminsional feature.
+All quantized features are concatenated to form a 1384 dimensional feature.
+These low-level features are generated for training and testing datasets using the entire image.
+This is done to avoid introducing any feature artifacts as a result of black space surrounding segmented regions.
 
-For training, we use SVM classifier with Gaussian kernel to train
-model for each attribute.
+For training, we use an SVM classifier with a Gaussian kernel to train
+the model for each attribute.
 
@@
 produces a hierarchical segmentation by first detecting contours
-using the \emph{gPb} detector \cite{maire08}.  Once the contours are
+using the \emph{gPb} detector \cite{maire08}.  This contour detector
+is advantageous because it uses brightness, color and texture
+gradients at multiple scales.  Once the contours are
 detected, regions are discovered using a watershed algorithm after
@@
 the root node in the segmentation tree.  The next level of the tree is
-found by thresholding the UCM at the next highest intensity and so on.
+found by thresholding the two new regions of the UCM at each, respective,
+next highest intensity and so on.
 Figure \ref{fig:ucm} shows an example UCM image and figure \ref{fig:tree}
@@
 
-Our objective is to detect objects and segment them out. In our
-segmentation tree, the problem changes to how to select
-those nodes belong to the desired object. We estimate the
-probability that a node is belong to object based on the attribute
-confidence distribution. For each object, we manually give the
-desired attribute distribution by common knowledge. We use the
+Our objective is to detect objects and segment them out. Using a segmentation tree
+we cast the problem into one of selecting nodes that belong 
+to the desired object. We estimate the
+probability that a node belongs to object based on the attribute
+confidence distribution. For each object, we manually determine a
+canonical attribute distribution.  We use the
 histogram intersection between the desired distribution and the
@@
 
-To select the nodes, we propose two different top-down prune algorithms, additive algorithm and subtractive algorithm.
-We use the UCM to generate two types of region tree, shown in figure \ref{fig:tree}.
-The first tree is an additive tree, where regions are subdivided into successively
-smaller regions moving down in the tree.  We call it ``additive'' because the
-original image can be reconstructed by adding the regions from each leaf node
-together.  The figures show the nodes of the trees as containing images, but in
-truth the trees contain binary masks which, when applied to the original image,
-produce the shown node contents.
-
-The second tree is ``subtractive.''  The tree has identical structure to the additive
-tree and each node contains the inverse of the mask of the corresponding node
-in the additive tree.
-
-The final segmentation is obtained by pruning the region tree until a final segmentation
-meeting some criterion of absolute or relative attribute saliency is found.
-We have two methods for pruning the tree, each showing relative strengths and
-weakness.  The first is a semi-greedy additive approach which uses the additive
-tree.  The second is a greedy subtractive approach.  We now discuss each of these
-in detail.
+To select the nodes, we use two different top-down pruning algorithms, 
+the ``additive'' algorithm and the ``subtractive'' algorithm. 
+Each of these algorithms prunes the region tree until a final segmentation
+meeting some criterion of absolute or relative attribute similarity to the canonical is found.
+We now discuss each algorithm in detail.
 
@@
 
-In this section, we evaluate our attribute based object detection
-and segmentation algorithm. We will answer four questions. (1) What
-is the performance of object detection and segmentation? (2) What is
-the influences of different parameters? (3) What are the advantages
-of the two pruning algorithms? (4) Is vertical confidence
-propagation useful? (In this draft, we only have partial results, so
-not all the questions are considered.)
+In this section, we evaluate our attribute based object classification
+and segmentation algorithm. We will also analyse the advantages and disadvantages of out algorithm.\\
 
-%\subsection{Dataset}
-%\label{ssec:dataset}
+\subsection{Dataset}
+\label{ssec:dataset}
 
-We use the Pascal2008 dataset. This dataset has a lot of real life
+We use the Pascal2008 dataset for both training and testing. This dataset has a lot of real life
 images which are more difficult to classify. The objects are labeled
@@
 bounding boxes are not a good measure of segmentation truth, but
-it's the best we have available.
+it's the best we have available.\\
 
-The segmentation precision for the additive algorithm
-is far better than the precision for the subtractive algorithm (which averaged
-0.09).  This is because the additive algorithm only segments images for
-which it has predicted presence of a car, so that any image pruned by the
-algorithm already has a high car similarity score, enhancing the segmentation.
-The subtractive algorithm, on the other hand, assumes presence of a car in
-the image and proceeds no matter how poor the initial similarity score is.
-(For the final paper we expect to have results comparing the precision
-of the two algorithms based only on images segmented by both.)
+\subsection{Classification}
+\label{ssec:classification}
 
-Figures \ref{fig:good_results} and \ref{fig:bad_results} show the
-results of segmentations of various images by both pruning
+Table \ref{table:aresults} shows the classification results comparing the proposed method with 
+the other three baseline methods. LowFea means that we use the low level feature to train and test 
+the object classification directly. Att1 means that we use the attribute distribution as the feature,
+but we only test it in the whole image without segmentation. Random means random prediction. Add is our
+proposed algorithm with additive pruning. The proposed algorithm has the highest precision comparing 
+with the other baselines, while the recall is a little lower than LowFea. Figure \ref{fig:roc_class} 
+shows the ROC curve for each class and the average.\\
+
+\begin{table}
+\centering
+\begin{tabular}{|l|l|l|}
+\hline Methods & Precision(\%) & Recall(\%) \\
+\hline LowFea  & 55.97 & 70.96 \\
+\hline Att1    & 51.89 & 51.89 \\
+\hline Random  & 35.19 & 50.00 \\
+\hline Add     & 60.82 & 54.06 \\
+\hline
+\end{tabular}
+\caption{Object classification results of three baseline methods and the proposed additive algorithm.}
+\label{table:aresults}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/add_res/roc_class.png.eps}
+\caption{Result of adjusting the factor $f$ in the subtractive
+algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
+and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
+that \subref{fig:fb} retains more of the cars, especially the two
+closest on the right and left, but also has more false-positive
+pixels, such as the ceiling region of the parking garage.}
+\label{fig:roc_class}
+\end{figure}
+
+\subsection{Segmentation}
+\label{ssec:segmentation}
+
+Figure \ref{fig:roc_seg} shows the segmentation precision of additive pruning 
+versus the false positive rate of object classification. The segmentation precision
+is in the range of $20\%$ to $50\%$. Some of the segmentation results are shown in 
+Figure \ref{fig:car_good_results},\ref{fig:car_bad_results},\ref{fig:aeroplane_good_results},\ref{fig:aeroplane_bad_results},\ref{fig:horse_good_results},\ref{fig:horse_bad_results}.\\
+
+Figures \ref{fig:car_good_results} and \ref{fig:car_bad_results} show the
+segmentations of car images by both additive and subtractive pruning
 algorithms. Figure \ref{fig:good_results} shows some good results,
@@
 shots, although rear shots performed reasonably well when tail
-lights were not illuminated.
+lights were not illuminated.\\
 
-\begin{table}
+Figures \ref{fig:aeroplane_good_results}, \ref{fig:aeroplane_bad_results} and 
+\ref{fig:horse_good_results}, \ref{fig:horse_bad_results} show some good and bad 
+segmentation results of additive algorithm on aeroplane and horse classes. Because of the
+high complexity of the subtractive algorithm, we did not run it on these two classes. The good 
+results are accurate to segment out the objects. One important note is that our algorithm can segment out
+multiple objects at the same time. The bad segmentations either miss 
+part of the object or contain so much background. The bad ones are caused 
+by two reasons. First, the hierarchical segmentation tree is not fine enough. We did not use all 
+levels in the segmentation tree. The more levels we use, the more time we need to spend on it. 
+Also when the segments are too small, the attribute detection is nearly random, because the small regions 
+do not have enough points to represent their properties. Second, the training of attributes based on
+bounding boxes is not accurate, because of many background pixels can be included in the bounding boxes. 
+This is especially obvious to the horse images, since horses are not convex enough in the images. 
+All the segmented images in figure \ref{fig:horse_bad_results} contains grass or trees, especially the 
+left one which only contains grass. These images prove that the grass or trees models are actually
+included in the horse model.\\
+
+\begin{figure}
 \centering
-\begin{tabular}{|l|l|l|}
-\hline Parameter & recall & prec \\
-\hline 0.8,0.4,0.1  & 0.4317 & 0.2393 \\
-\hline 0.8,0.4,0.15  & 0.3849 & 0.2370 \\
-\hline 0.8,0.6,0.15  & 0.2720 & 0.2501 \\
-\hline
-\end{tabular}
-\caption{Results from the additive algorithm on all car images.
-Parameter contains the three threshold, $thre\_perf$, $thre\_pos$
-and $thre\_neg$, recall is the object detection recall rate and prec
-is the segmentation precision on all detected images.}
-\label{table:aresults}
-\end{table}
+\includegraphics[width=0.5\textwidth]{figures/add_res/roc_seg.png.eps}
+\caption{Result of adjusting the factor $f$ in the subtractive
+algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
+and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
+that \subref{fig:fb} retains more of the cars, especially the two
+closest on the right and left, but also has more false-positive
+pixels, such as the ceiling region of the parking garage.}
+\label{fig:roc_seg}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/SubSegPrec.eps}
+\caption{Graph of the precision of the subtractive segmentation
+algorithm against confidence, or attribute similarity.  Despite
+the noise, there is an upward trend in the precision
+as the similarity score increases, as shown by the 
+quadratic least-squares fit.}
+\label{fig:sub_seg_prec}
+\end{figure}
+
+%\begin{figure*}[p]
+%\centering
+%\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+%\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
+%\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
+%\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
+%\end{tabular}
+%\caption{Selected results from segmentation of cars from the Pascal2008
+%dataset.  The first row shows the original image.  The second row shows
+%the best segmentation from the additive algorithm.  The third row shows
+%the segmentation from the subtractive algorithm with $f=0.9$.}
+%\label{fig:good_results}
+%\end{figure*}
+
+%\begin{figure*}[p]
+%\centering
+%\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
+%\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
+%\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
+%Car not detected &
+%\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
+%\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
+%\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
+%\end{tabular}
+%\caption{Selected results from segmentation of cars from the Pascal2008
+%dataset.  The first row shows the original image.  The second row shows
+%the best segmentation from the additive algorithm.  The third row shows
+%the segmentation from the subtractive algorithm with $f=0.9$.}
+%\label{fig:bad_results}
+%\end{figure*}
 
@@
 \centering
-\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
-\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
-\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
-\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_007064.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_000052.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_007171.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_000251.jpg.eps} \\
+
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_007064.jpg_1_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_000052.jpg_1_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_007171.jpg_1_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/car/2008_000251.jpg_1_good.jpg.eps} \\
+
+\includegraphics[width=2.95cm]{figures/sub_results/2008_007064_1_bad_sub.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/sub_results/2008_000052_1_bad_sub.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/sub_results/2008_007171_1_bad_sub.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/sub_results/2008_000251_1_bad_sub.jpg.eps} \\
 \end{tabular}
@@
 the segmentation from the subtractive algorithm with $f=0.9$.}
-\label{fig:bad_results}
+\label{fig:car_bad_results}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:aeroplane_good_results}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:aeroplane_bad_results}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:horse_good_results}
+\end{figure*}
+
+\begin{figure*}[p]
+\centering
+\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
+\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
+\end{tabular}
+\caption{Selected results from segmentation of cars from the Pascal2008
+dataset.  The first row shows the original image.  The second row shows
+the best segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm with $f=0.9$.}
+\label{fig:horse_bad_results}
 \end{figure*}

### 2010-05-12 paper.tex
changes

@@
 \subsection{Subtractive algorithm}
+\label{sec:sub}
 
@@
 \begin{algorithmic}
+  \STATE \textbf{global:}
+  \STATE \hspace{3 mm} master mask $m_m$
   \STATE \textbf{input:}
   \STATE \hspace{3 mm} node $n$ in segmentation tree
-  \STATE \hspace{3 mm} master mask $m_m$
   \STATE \hspace{3 mm} similarity $sim_{root}$ on root node
@@
   %\STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
-  \IF{$sim < f sim_{root}$}
+  \IF{$sim < f \cdot sim_{root}$}
     \FOR{$i=1$ to $n.childNum$}
-      \STATE s\{i\}=SUBTRACTIVE\_PRUNE(n.children\{i\},$m_m$,
+      \STATE SUBTRACTIVE\_PRUNE(n.children\{i\},
       \STATE ...$sim_{root}$, $f$)
@@
 example is figure \ref{fig:truck}, where the two cars visually behind the truck
-are segmented alongside the truck.
+are segmented together with the truck.
 
@@
 In this section, we evaluate our attribute based object classification
-and segmentation algorithm. We will also analyse the advantages and disadvantages of out algorithm.\\
+and segmentation algorithms. We also analyze the advantages and 
+disadvantages of our algorithms.\\
 
@@
 
-We use the Pascal2008 dataset for both training and testing. This dataset has a lot of real life
-images which are more difficult to classify. The objects are labeled
-by bounding boxes not accurate segmentation. For training the
-attributes, we use the pascal2008 training set. The attribute
+We used the Pascal2008 dataset for both training and testing. This dataset contains real life
+images which are generally difficult to classify. 
+For training and testing of classification and
+segmentation we used the pascal2008 training and validation sets, respectively.
+The objects are labeled
+by bounding boxes -- unfortunately accurate segmentations are not available
+with this dataset.  The attribute
 annotations used in \cite{farhadi09} are freely available and we
-used them for training too. For testing the classification and
-segmentation, we use the pascal2008 validation set. Three classes are used in this experiment, including car,
-aeroplane and horse. We get 328 testing images, with car 150, aeroplane 103 and horse 93. Note that one image 
-can contain multiple objects in multiple classes.\\
+used them for both training and testing. Three classes are used in this experiment, including car,
+airplane and horse. We used 328 test images, with 150 car, 103 airplane and 93 horse. 
+Note that any given image may
+contain multiple objects in multiple classes.\\
 
@@
 with the other baselines, while the recall is a little lower than LowFea. Figure \ref{fig:roc_class} 
-shows the ROC curve for each class and the average.\\
+shows the ROC curve for each class and the average.
+
+The subtractive algorithm is not included in classification results as it performs no
+object detection or classification and assumes that the given object is present
+in the image.
 
@@
 is in the range of $20\%$ to $50\%$. Some of the segmentation results are shown in 
-Figure \ref{fig:car_good_results},\ref{fig:car_bad_results},\ref{fig:aeroplane_good_results},\ref{fig:aeroplane_bad_results},\ref{fig:horse_good_results},\ref{fig:horse_bad_results}.\\
+Figure \ref{fig:car_good_results},\ref{fig:car_bad_results},\ref{fig:aeroplane_good_results},\ref{fig:aeroplane_bad_results},\ref{fig:horse_good_results},\ref{fig:horse_bad_results}.
+Again, the subtractive algorithm doesn't produce
+analogous results as it performs no classification.
+
+Figure \ref{fig:sub_seg_prec} shows a plot of segmentation precision against 
+attribute similarity for the subtractive algorithm.  As discussed in section 
+\ref{sec:sub}, the original image (the root node of the segmentation tree)
+is given an attribute similarity score compared to the canonical.  This score
+drives the subtractive algorithm, and the final segmentation can have a score
+no lower than $f\cdot sim_{root}$.  The figure shows the final segmentation's
+similarity score along the x-axis and the segmentation precision on the y-axis.
+As expected, as the similarity score (or confidence in the existence of the
+object) increases, the quality of the segmentation also increases.
 
@@
 segmentations of car images by both additive and subtractive pruning
-algorithms. Figure \ref{fig:good_results} shows some good results,
-while Figure \ref{fig:bad_results} shows some bad results. This
-shows clear linkage between prominence of the side profile of the
-car and success of the segmentation. It appears that the attribute
-classifiers are more accurate on side profiles than front and rear
-shots, although rear shots performed reasonably well when tail
-lights were not illuminated.\\
+algorithms. These show that it is somewhat unclear which pruning algorithm
+gives the best performance (although a precision measure could be used if we
+had better ground truth data).  But the results show some interesting patterns.
+In general, the subtractive algorithm tends to produce more fragmented results
+than the additive.  This is because the pruning algorithm searches all the way
+to the bottom of the segmentation tree searching for regions that can be removed.
+There are various techniques that could fix this, such as doing some kind of
+confidence propagation from a ``good'' node to its descendents, in a similar
+spirit to \cite{borenstein04}.  But while the additive algorithm does tend
+to retain large portions of the car, it is often far too conservative, as
+can be seen in figure \ref{fig:car_bad_results}.  Of course, this can be 
+fixed by adjusting the threshold parameters, but this puts too much responsibility
+on parameter selection for specific cases and causes it to not generalize well.
 
@@
 \ref{fig:horse_good_results}, \ref{fig:horse_bad_results} show some good and bad 
-segmentation results of additive algorithm on aeroplane and horse classes. Because of the
-high complexity of the subtractive algorithm, we did not run it on these two classes. The good 
-results are accurate to segment out the objects. One important note is that our algorithm can segment out
-multiple objects at the same time. The bad segmentations either miss 
-part of the object or contain so much background. The bad ones are caused 
-by two reasons. First, the hierarchical segmentation tree is not fine enough. We did not use all 
-levels in the segmentation tree. The more levels we use, the more time we need to spend on it. 
-Also when the segments are too small, the attribute detection is nearly random, because the small regions 
-do not have enough points to represent their properties. Second, the training of attributes based on
+segmentation results of the additive algorithm on airplane and horse classes. Because of the
+high complexity of the subtractive algorithm, we did not run it on these two classes. 
+Figures \ref{fig:aeroplane_good_results} and \ref{fig:horse_good_results} show some
+of the more impressive segmentations.  The third column in each figure shows that
+the algorithm segments out multiple objects at the same time.
+
+Figures \ref{fig:aeroplane_bad_results} and \ref{fig:horse_bad_results} show results
+that either miss part of the object or contain a lot of background.  Extreme cases,
+such as the second image in \ref{fig:horse_bad_results} mask out the object of interest
+(horse, in this case) and almost nothing else.  These errors are cause by two things:
+first, the additive algorithm currently does not use all levels in the segmentation tree,
+as it would have made testing take prohibitively long.
+Another problem with searching deep in the tree is that when the segments are too small, 
+the attribute detection is nearly random, because the small regions 
+don't have enough points to represent their properties. Second, the training of attributes based on
 bounding boxes is not accurate, because of many background pixels can be included in the bounding boxes. 
-This is especially obvious to the horse images, since horses are not convex enough in the images. 
+This is especially obvious to the horse images, since horses are far from having a convex shape. 
 All the segmented images in figure \ref{fig:horse_bad_results} contains grass or trees, especially the 
-left one which only contains grass. These images prove that the grass or trees models are actually
+left one which only contains grass. These images imply that the grass and tree models are actually
 included in the horse model.\\
@@
 the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f=0.9$.}
+the segmentation from the subtractive algorithm with $f$ at different values
+between 0.9 and 1.0.}
 \label{fig:car_good_results}
@@
 the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f=0.9$.}
+the segmentation from the subtractive algorithm with $f$ at different values
+between 0.9 and 1.0.}
 \label{fig:car_bad_results}
@@
 \end{tabular}
-\caption{Selected results from segmentation of cars from the Pascal2008
+\caption{Selected results from segmentation of planes from the Pascal2008
 dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f=0.9$.}
+the best segmentation from the additive algorithm.}
 \label{fig:aeroplane_good_results}
@@
 \end{tabular}
-\caption{Selected results from segmentation of cars from the Pascal2008
+\caption{Selected results from segmentation of planes from the Pascal2008
 dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f=0.9$.}
+the best segmentation from the additive algorithm.}
 \label{fig:aeroplane_bad_results}
@@
 \end{tabular}
-\caption{Selected results from segmentation of cars from the Pascal2008
+\caption{Selected results from segmentation of horses from the Pascal2008
 dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f=0.9$.}
+the best segmentation from the additive algorithm.}
 \label{fig:horse_good_results}
@@
 \end{tabular}
-\caption{Selected results from segmentation of cars from the Pascal2008
+\caption{Selected results from segmentation of horses from the Pascal2008
 dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f=0.9$.}
+the best segmentation from the additive algorithm.}
 \label{fig:horse_bad_results}
@@
 \label{sec:discussion}
+
+USE SUBTRACTIVE WITH ADDITIVE, FIX SUBTRACTIVE FRAGMENTATION
+
 It can be seen that in simple cases both additive and subtractive algorithms

### 2010-05-12 trunk/paper.tex
updated paper

@@
 \begin{abstract}
-Attributes have been shown to be effective in assisting object detection and
+Attributes have been shown to be effective in assisting object classification and
 classification, and they provide means to also incorporate semantic
@@
 features.  The attributes of an image are learned using low-level features,
-and once learned, they can be used in object detection and also in describing
+and once learned, they can be used in object classification and also in describing
 objects in an image that are unknown.
@@
 
-\section{Object Detection and Segmentation}
+\section{Object Classification and Segmentation}
 \label{sec:detection}
@@
 
-The object detection is based on the output of ADDITIVE\_PRUNE.
+The object classification is based on the output of ADDITIVE\_PRUNE.
 If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.
-
-(We also plan to do the vertical confidence propogation. But due to the slowness of the experiment, we cannot incorporate it in this draft. We will show it in the final paper.)
 
@@
 \label{fig:roc_seg}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/SubSegPrec.eps}
+\caption{Graph of the precision of the subtractive segmentation
+algorithm against confidence, or attribute similarity.  Despite
+the noise, there is an upward trend in the precision
+as the similarity score increases, as shown by the 
+quadratic least-squares fit.}
+\label{fig:sub_seg_prec}
 \end{figure}
@@
 
-As object detection is generally only as good as the features used, so also it
+As object classification is generally only as good as the features used, so also it
 appears that this approach to segmentation is only as good as the attribute

### 2010-05-12 trunk/paper.tex
changes

@@
 The idea is to find image regions with attribute distributions very similar
-to some canonical distribution for an object.  We define the ``canonical distribution''
+to some canonical distribution for an object.  Figure \ref{fig:truck} shows
+an example.  We define the ``canonical distribution''
 to be an attribute distribution representative of that object.  For example, the
@@
 
-We note that it is possible that one segmented region may contain the object and
-nothing else.  Though possible, in practice it is highly unlikely.  Even for rather
-simple objects, the true region of the object is distributed among various
-segmentations.  This is because all but the most trivial objects have different
-sub-regions of different colors, textures, contours, etc.  Thus we must search
-for a combination of these sub-regions that make up the object.
+%We note that it is possible that one segmented region may contain the object and
+%nothing else.  Though possible, in practice it is highly unlikely.  Even for rather
+%simple objects, the true region of the object is distributed among various
+%segmentations.  This is because all but the most trivial objects have different
+%sub-regions of different colors, textures, contours, etc.  Thus we must search
+%for a combination of these sub-regions that make up the object.
 
@@
 this paper, but without discarding the hierarchy.
-Russell et al \cite{russell06} detect the whole object in each of
-the multiple segment, by assuming that most objects get segmented
-correctly at least once during the multiple segmentation. Our approach
-will be far less aggressive in that we will use object classes and
-features (attributes in our case) that are known \emph{a priori}.
+
+Russell et al \cite{russell06} attempt object classification 
+by assuming that most objects get segmented
+correctly at least once during the multiple segmentation. We make no such
+assumption.  Rather, we find some region that contains the entire
+object (which may be the original image) and refine that rough
+segmentation.  Russell et all also learn object classes in an
+unsupervised manner.  Our approach
+will be far less aggressive in that we will use object classes 
+that are known \emph{a priori}.
 Pantofaru et
@@
 Three different type of features are used: HOG, texture and color descriptors \cite{farhadi09}.  
-We use kmeans to quantize the features.
-The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively.
+We use kmeans to quantize the features. The HOG descriptors are quantized into 1000 clusters, 
+and the texture and color are quantized to 256 and 128 clusters, respectively. 
 All quantized features are concatenated to form a 1384 dimensional feature.
-These low-level features are generated for training and testing datasets using the entire image.
-This is done to avoid introducing any feature artifacts as a result of black space surrounding segmented regions.
+Since all features are local, we represent a segment by using only features inside the segment
+to produce a feature histogram.  In other words, rather than segmenting the image and finding features,
+we find features and then segment the features.
+This is done to avoid introducing any feature artifacts as a result of black space surrounding 
+segmented regions in the image.
 

### 2010-05-12 paper.tex
paper updated

@@
 
-As object detection is generally only as good as the features used, so also it
-appears that this approach to segmentation is only as good as the attribute
-selection and training.  We found that in images with poor segmentations, the
-confidences in prediction of car attributes were generally low.  One problem
-with this implementation of attribute classifiers was that we didn't use
-the selection criterion described in \cite{farhadi09} that enhances within
-category prediction ability.  This means that, for example, the wheel attribute
-is highly similar to the car attribute and thus its discrimative ability
-is hurt.  One future direction for this research would be to improve the attribute
-training using the additional selection criterion and observe effects on
-the segmentations.
-
 An interesting orthogonal direction that could be taken with these ideas is to
@@
 numbers of images even if no detection of their desired object exists.
+
+As object classification is generally only as good as the features used, so also it
+appears that this approach to segmentation is only as good as the attribute
+selection and training.  We found that in images with poor segmentations, the
+confidences in prediction of object-related attributes were generally low. The bounding 
+boxes groundtruth can include many background features into the attribute models. Those 
+features are very harmful. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
+which only segments out the background grass. However, even if we have the segmentation 
+of objects as the groundtruth for training the attributes, we may still not have accurate 
+models, since the groundtruth is for objects not for attributes. For example, if we train 
+the attributes of wheel or metal only based on car images, we may get the car model not 
+the attributes model. One way to deal with this problem is to directly label attributes 
+groundtruth. Then we can get similar accurate attribute models as the object models.
 

### 2010-05-12 paper.tex
changes

@@
 
-USE SUBTRACTIVE WITH ADDITIVE, FIX SUBTRACTIVE FRAGMENTATION
-
 It can be seen that in simple cases both additive and subtractive algorithms
@@
 
-The holy grail of this approach, of course, is to be able to segment objects
-for which the canonical attribute distribution is unknown, based on a measure
-of attribute coherence.  If this can be achieved, then segmentation experiments
-could open up to non-experts, who could define coherence measures based on
-semantic attributes and then could use this approach to automatically segment large
-numbers of images even if no detection of their desired object exists.
-
 As object classification is generally only as good as the features used, so also it
@@
 selection and training.  We found that in images with poor segmentations, the
-confidences in prediction of object-related attributes were generally low. The bounding 
-boxes groundtruth can include many background features into the attribute models. Those 
-features are very harmful. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
+confidences in prediction of object-related attributes were generally low. Using bounding 
+boxes as ground truth can introduce many background features into the attribute models. These 
+features can be harmful. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
 which only segments out the background grass. However, even if we have the segmentation 
-of objects as the groundtruth for training the attributes, we may still not have accurate 
-models, since the groundtruth is for objects not for attributes. For example, if we train 
+of objects as the ground truth for training the attributes, we may still not have accurate 
+models, since the ground truth is for objects not for attributes. For example, if we train 
 the attributes of wheel or metal only based on car images, we may get the car model not 
 the attributes model. One way to deal with this problem is to directly label attributes 
-groundtruth. Then we can get similar accurate attribute models as the object models.
+ground truth. Then we can get similar accurate attribute models as the object models.
 
@@
 do the object classification, we cannot separate dog and cat, since both of them have all of the attributes. 
-But those attributes can definitely separate the two objects from non-animal objects, such as car. This example demonstrates that 
-attributes are helpful for the object classification, but they are not discriminative enough. So one way to deal with this is to use 
-both attributes features and low level objects features for object classification. We can train a general attributes models first. 
+But those attributes can definitely separate the two objects from non-animal objects, such as car. So
+attributes are helpful for object classification, but they are often not discriminative enough. One way to deal with this is to use 
+both attributes features and low level objects features for object classification. We can train general attributes models first. 
 When we want to classify some specific objects, we can incorporate a small number of low level features from the specific object samples to the attributes 
 features. In this way, we both reduce the training samples for object classification, and make the attribute based method more discriminative.
+
+Interestingly, the region pruning algorithms are feature-type independent.  That
+is, they are not necessarily wedded to attribute features and could be used with
+any feature type given a similarity scoring function.  Interesting future work would
+be to try the pruning methods with lower-level features.
+
+The holy grail of this approach, of course, is to be able to segment any object
+with a given canonical attribute distribution.  If this can be achieved, 
+then segmentation experiments
+could open up to non-experts, who could define an attribute distribution
+based on their own knowledge and use a system that has already been trained
+on a large number of attributes to segment the object.
 

### 2010-05-12 trunk/paper.tex
paper looks good

@@
 \end{tabular}
-\caption{Object classification results of three baseline methods and the proposed additive algorithm.}
+\caption{Object classification results of three baseline methods(LowFea, Att1 and Random) and the proposed additive algorithm(Add).}
 \label{table:aresults}
@@
 \includegraphics[width=0.5\textwidth]{figures/add_res/roc_class.png.eps}
-\caption{Result of adjusting the factor $f$ in the subtractive
-algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
-and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
-that \subref{fig:fb} retains more of the cars, especially the two
-closest on the right and left, but also has more false-positive
-pixels, such as the ceiling region of the parking garage.}
+\caption{ROC curves for object classification of car, aeroplane, horse and average.}
 \label{fig:roc_class}
@@
 \includegraphics[width=0.5\textwidth]{figures/add_res/roc_seg.png.eps}
-\caption{Result of adjusting the factor $f$ in the subtractive
-algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
-and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
-that \subref{fig:fb} retains more of the cars, especially the two
-closest on the right and left, but also has more false-positive
-pixels, such as the ceiling region of the parking garage.}
+\caption{The curve of segmentation precision versus false positive classification rate.}
 \label{fig:roc_seg}
@@
 \end{tabular}
-\caption{Selected results from segmentation of cars from the Pascal2008
-dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f$ at different values
-between 0.9 and 1.0.}
+\caption{Selected results from segmentation of cars, which additive algorithm performs good.
+  The first row shows the original image.  The second row shows
+the segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm.}
 \label{fig:car_good_results}
@@
 \end{tabular}
-\caption{Selected results from segmentation of cars from the Pascal2008
-dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.  The third row shows
-the segmentation from the subtractive algorithm with $f$ at different values
-between 0.9 and 1.0.}
+\caption{Selected results from segmentation of cars, which subtractive algorithm performs good. 
+ The first row shows the original image.  The second row shows
+the segmentation from the additive algorithm.  The third row shows
+the segmentation from the subtractive algorithm.}
 \label{fig:car_bad_results}
@@
 \end{tabular}
-\caption{Selected results from segmentation of planes from the Pascal2008
-dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.}
+\caption{Selected good results from segmentation of aeroplanes.  
+The first row shows the original image.  The second row shows
+the segmentation from the additive algorithm.}
 \label{fig:aeroplane_good_results}
@@
 \end{tabular}
-\caption{Selected results from segmentation of planes from the Pascal2008
-dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.}
+\caption{Selected bad results from segmentation of aeroplanes.
+ The first row shows the original image.  The second row shows
+the segmentation from the additive algorithm.}
 \label{fig:aeroplane_bad_results}
@@
 \end{tabular}
-\caption{Selected results from segmentation of horses from the Pascal2008
-dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.}
+\caption{Selected good results from segmentation of horses.  
+The first row shows the original image.  The second row shows
+the segmentation from the additive algorithm.}
 \label{fig:horse_good_results}
@@
 \end{tabular}
-\caption{Selected results from segmentation of horses from the Pascal2008
-dataset.  The first row shows the original image.  The second row shows
-the best segmentation from the additive algorithm.}
+\caption{Selected bad results from segmentation of horses.  
+The first row shows the original image.  The second row shows
+the segmentation from the additive algorithm.}
 \label{fig:horse_bad_results}
@@
 \label{sec:discussion}
-
-USE SUBTRACTIVE WITH ADDITIVE, FIX SUBTRACTIVE FRAGMENTATION
 
@@
 
-As object classification is generally only as good as the features used, so also it
-appears that this approach to segmentation is only as good as the attribute
-selection and training.  We found that in images with poor segmentations, the
-confidences in prediction of car attributes were generally low.  One problem
-with this implementation of attribute classifiers was that we didn't use
-the selection criterion described in \cite{farhadi09} that enhances within
-category prediction ability.  This means that, for example, the wheel attribute
-is highly similar to the car attribute and thus its discrimative ability
-is hurt.  One future direction for this research would be to improve the attribute
-training using the additional selection criterion and observe effects on
-the segmentations.
-
 An interesting orthogonal direction that could be taken with these ideas is to
@@
 
-The holy grail of this approach, of course, is to be able to segment objects
-for which the canonical attribute distribution is unknown, based on a measure
-of attribute coherence.  If this can be achieved, then segmentation experiments
-could open up to non-experts, who could define coherence measures based on
-semantic attributes and then could use this approach to automatically segment large
-numbers of images even if no detection of their desired object exists.
+As object classification is generally only as good as the features used, so also it
+appears that this approach to segmentation is only as good as the attribute
+selection and training.  We found that in images with poor segmentations, the
+confidences in prediction of object-related attributes were generally low. Using bounding 
+boxes as ground truth can introduce many background features into the attribute models. These 
+features can be harmful. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
+which only segments out the background grass. However, even if we have the segmentation 
+of objects as the ground truth for training the attributes, we may still not have accurate 
+models, since the ground truth is for objects not for attributes. For example, if we train 
+the attributes of wheel or metal only based on car images, we may get the car model not 
+the attributes model. One way to deal with this problem is to directly label attributes 
+ground truth. Then we can get similar accurate attribute models as the object models.
 

### 2010-05-12 paper.tex
changes

@@
 \begin{abstract}
-Attributes have been shown to be effective in assisting object classification and
-classification, and they provide means to also incorporate semantic
+Attributes have been shown to be effective in assisting object classification, and they provide means to also incorporate semantic
 information available to and provided by humans.  On another front, the
@@
 other measure of ``window'' and so forth.  If
-regions can be combined together to for larger regions with attribute
+regions can be combined together into larger regions with attribute
 distributions matching the object's canonical distribution then one can
@@
 One algorithm is additive and operates by combining regions that are likely
-to be part of the object.  The other is subtractive, which first predict attributes on
+to be part of the object.  The other is subtractive, which first predicts attributes on
 the entire region and then proceeds by observing the effects of
@@
 $O(n)$ where $n$ is the number of leaves in the segmentation tree.
-The flowchart of our algorithm is shown in Figure
+The high-level outline of our algorithm is shown in Figure
 \ref{fig:flowchart}.
-
-This work is done using attributes as the features, but the segmentation
-pruning algorithms are actually feature-type agnostic and could be used
-with any image feature given a scoring function applicable to that feature.
 
@@
 Attributes are high-level features which can reflect semantic properties of objects.
-Given the attributes, we can do object detection based on their distribution.
+Given the attributes, we can perform object classification based on an image's attribute distribution.
 We use the same attribute set as \cite{farhadi09}.
@@
 
-We use a similar algorithm to that used in \cite{farhadi09} to train the attribute models. 
+We use a similar approach to that used in \cite{farhadi09} to train the attribute models. 
 Three different type of features are used: HOG, texture and color descriptors \cite{farhadi09}.  
@@
 representative of the region's location in the hierarchy.  So to find
-the first branch in the tree, threshold the UCM image with a value
-$t$ where $t = max{I(x,y)}$ where $I(x,y)$ is the intensity at pixel
+the first branch in the tree, we threshold the UCM image with a value
+$t$ where $t = max\{I(x,y)\}$ where $I(x,y)$ is the intensity at pixel
 location $(x,y)$.  The thresholded image can then be flood-filled into
@@
 the attributes in each node, including the intermediate and
-leaf nodes. We use the output of SVM as the confidence (not binary),
+leaf nodes. We use the output of the SVM as the confidence (not binary),
 so each node can be represented by the confidence distribution of
@@
 the additive pruning algorithm.  Unfortunately the subtractive algorithm
-requires runtime predictions, and thus cannot use this preprocessing
+requires runtime predictions, and thus cannot take advantage of this preprocessing
 step.
@@
 canonical attribute distribution.  We use the
-histogram intersection between the desired distribution and the
+histogram intersection between the canonical distribution and the
 estimated confidence distribution in each node as the similarity
@@
 \[ HI(H_{model},H_{pred}) = \frac{|H_{model} \cap H_{pred}|}{|H_{model}|}
-\] ,
-
+\]
 where $H_{model}$ and $H_{pred}$ represent the desired attribute
@@
 The idea of the algorithm is to find the smallest discriminative
-regions, either positive or negative. We combine all the smallest
-positive regions while remove all the negative ones to form the
-final segmentation. We use three threshold for the similarity
+regions, either positive or negative. We combine all 
+positive regions while removing all negative ones to form the
+final segmentation. We use three thresholds for the similarity
 measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent
@@
 respectively. If the similarity is above $thre\_perf$, which means
-the segmentation is perfect for the object, we cut all the nodes
-below and return this segment. If the similarity is below
+the segmentation is perfect for the object, we cut all descendent nodes
+and return this segment. If the similarity is below
 $thre\_neg$, which means the segment does not contain the object, we
-cut all the nodes below and return NULL. If the similarity is
+cut all descendent nodes and return NULL. If the similarity is
 between $thre\_perf$ and $thre\_pos$, which means the node
 definitely contains the object but the segmentation is not perfect
-yet, we keep on checking its children nodes to refine the
+yet, we check its children nodes to refine the
 segmentation. The final case is that the similarity is between
 $thre\_pos$ and $thre\_neg$, which means we are not sure whether
-there is an object in the node, so we just keep on searching its
+there is an object in the node, so we just search its
 children.
@@
 The object classification is based on the output of ADDITIVE\_PRUNE.
-If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.
+If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, then the object is detected in the image.
 
@@
 compared to the standard, then we assume that we can safely prune off the node's
-region without removing a part of the object..  If the
+region without removing a part of the object.  If the
 similarity was significantly affected, then we assume that the region
@@
 
-In this section, we evaluate our attribute based object classification
+In this section, we evaluate our attribute-based object classification
 and segmentation algorithms. We also analyze the advantages and 
@@
 Table \ref{table:aresults} shows the classification results comparing the proposed method with 
-the other three baseline methods. LowFea means that we use the low level feature to train and test 
+the other three baseline methods. LowFea means that we use the low level features to train and test 
 the object classification directly. Att1 means that we use the attribute distribution as the feature,
@@
 Figure \ref{fig:car_good_results},\ref{fig:car_bad_results},\ref{fig:aeroplane_good_results},\ref{fig:aeroplane_bad_results},\ref{fig:horse_good_results},\ref{fig:horse_bad_results}.
-Again, the subtractive algorithm doesn't produce
-analogous results as it performs no classification.
 
@@
 that either miss part of the object or contain a lot of background.  Extreme cases,
-such as the second image in \ref{fig:horse_bad_results} mask out the object of interest
-(horse, in this case) and almost nothing else.  These errors are cause by two things:
+such as the second image in figure \ref{fig:horse_bad_results} removes the object of interest
+(horse, in this case) and almost nothing else.  These errors are caused by two things:
 first, the additive algorithm currently does not use all levels in the segmentation tree,
-as it would have made testing take prohibitively long.
-Another problem with searching deep in the tree is that when the segments are too small, 
+as it would make testing take prohibitively long.
+Another problem with searching deep in the tree is that when the segments are too small
 the attribute detection is nearly random, because the small regions 
-don't have enough points to represent their properties. Second, the training of attributes based on
-bounding boxes is not accurate, because of many background pixels can be included in the bounding boxes. 
+don't have enough features to represent their attributes. Second, the training of attributes based on
+bounding boxes is not accurate, because many background pixels can be included in the bounding boxes. 
 This is especially obvious to the horse images, since horses are far from having a convex shape. 
@@
 
-It can be seen that in simple cases both additive and subtractive algorithms
+It can be seen that, in simple cases, both additive and subtractive algorithms
 are able to segment out rough outlines of the objects.  In most cases, even
-the more difficult ones, at least part of the car was present in the final
+the more difficult ones, at least part of the object was present in the final
 segmentation.  This shows that the segmentation algorithms appear to be
@@
 equally as important as shininess.  This gave unfair disadvantages to
-under-represented or ill-trained attributes.  This can be seen in the results
-where the body of the car is removed while the wheels or headlights are
-retained.
+under-represented or ill-trained attributes.
 
@@
 confidences in prediction of object-related attributes were generally low. Using bounding 
-boxes as ground truth can introduce many background features into the attribute models. These 
-features can be harmful. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
+boxes as ground truth can introduce many background features into the attribute models. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
 which only segments out the background grass. However, even if we have the segmentation 
 of objects as the ground truth for training the attributes, we may still not have accurate 
-models, since the ground truth is for objects not for attributes. For example, if we train 
-the attributes of wheel or metal only based on car images, we may get the car model not 
-the attributes model. One way to deal with this problem is to directly label attributes 
-ground truth. Then we can get similar accurate attribute models as the object models.
+models, since the ground truth is for objects, not for attributes. For example, if we train 
+the attributes of wheel or metal only based on car images, we may get the car model rather than 
+the attributes model. One way to deal with this problem is to directly label attributes' 
+ground truth. Then we can get similar accurate attribute models as the object models, although 
+it would be a tremendously time-consuming task to manually segment all attributes' regions.
 
@@
 
-The holy grail of this approach, of course, is to be able to segment any object
+The holy grail of our approach, of course, is to be able to segment any object
 with a given canonical attribute distribution.  If this can be achieved, 
